### 2021-03-24 proposal/proposal.tex
Initial Overleaf Import

% !TEX TS-program = pdflatexmk
\documentclass[11pt, letterpaper]{amsart}
%\usepackage{amsaddr}

\usepackage[isbn=false,url=false,doi=false,style=alphabetic]{biblatex} 
\addbibresource{sample.bib}

\usepackage{hyperref}

\usepackage{enumitem}
\setlist{itemsep=.5em, parsep = .5em} % < Usually a good idea

\title{Proposal for Term Paper: Bounds on Coding Theory from Algebraic Geometry}
\author{Guilherme Zeus Dantas e Moura}
%\address{Haverford College}
%\email{gdantasemo@haverford.edu}
%\date{Spring, 2021. Last change in \today}
\date{March 19, 2021}

\begin{document}

\maketitle

%\begin{abstract}    
%\end{abstract}

\section{Proposal of Topic}
    Coding theory is concerned with finding efficient ways to encode a message so that one may discover errors in the message --- and perhaps even correct. In algebraic coding theory, we study efficient codes generated from algebraic geometric methods.

    In my proposed paper, I plan on constructing the Reed-Solomon codes, generalizing them using projective curves, and understand the results from \cite{TVZ82} on finding a bound better than the well-known Gilbert--Varshamov bound.

\section{Outline}

\subsection{Coding theory} \label{ss:codingtheory}
First, we need to define what a \emph{code} is, as well as what does it mean for a code to be good. We shall define length $n$, dimension $k$, minimum distance $d$, code rate $R = n/k$, and relative minimum distance $\delta = d/n$.

\subsection{Singleton bound and a promising example} \label{ss:singleton}
We shall state and prove the Singleton Bound for linear codes (state and maybe prove for non-linear codes) and define maximum distance separable (MDS) codes. Then, define Reed--Solomon codes and show they meet the Singleton Bound, but have a limited length in comparison to the alphabet size.

\subsection{Generalized Reed-Solomon codes} \label{ss:grs}
We shall redefine the Reed--Solomon codes using language related to a projective line. There is a way to replace the ``projective line'' with a ``projective plane curve'' and create other codes, called \emph{Generalized Reed-Solomon codes} or simply \emph{algebraic geometric codes}. We want large $R$ and $\delta$, and these codes yield \begin{equation}\label{eq:g/n} R + \delta \ge 1 + 1/n - g/n,\end{equation} where $n$ is the number of rational points of a curve $X$, with genus $g$.

\subsection{Final thoughts} \label{ss:tvz} On equation \eqref{eq:g/n}, we observe that good algebraic geometric codes are generated by curves with a large ratio between $n$ and $g$. On \cite{TVZ82}, the authors present a sequence of such curves, with $n/g$ large enough to create a better bound than the Gilbert--Varshamov one.

\section{Annotated Bibliography}

\begin{enumerate}
    \item[\textbf{\cite{TVZ82}}] \fullcite{TVZ82}.

    My proposed paper is aimed towards understanding the results of this article, as we see in subsection \ref{ss:tvz}. However, its language is rather complicated and heavy on algebraic geometry, so I will need to use other sources to understand it.

    \item[\textbf{\cite{TVN07}}] \fullcite{TVN07}.

    This is a book written by the authors of the previous article, that starts Algebraic Coding Theory from the scratch; thus it is an amazing resource to understand the language used in \cite{TVZ82}. However, it is quite long and has a lot of information not directly related to \cite{TVZ82}; so I'll primarily use this source to search for definitions and details about terms I encounter elsewhere.

    \item[\textbf{\cite{Wal00}}] \fullcite{Wal00}.

    Aimed for undergraduates, this book explains definitions and motivations from coding theory (which correspond to subsections \ref{ss:codingtheory} and \ref{ss:singleton}); explains facts from algebraic geometry; describes the algebraic geometric codes; and discusses the results from \cite{TVZ82}.

    \item[\textbf{\cite{LS87}}] \fullcite{LS87}.

    This is an expository article that aims to simplify the methods from algebraic geometry used in \cite{TVZ82}. Their approach is similar to the one found in \cite{Wal00}, but it is much shorter and concise. It will be a great complement to the other sources.

\end{enumerate}

\end{document}

### 2021-03-29 draft/draft.tex
section 1 done

% !TEX TS-program = pdflatexmk
\documentclass[11pt, letterpaper]{amsart}
%\usepackage{amsaddr}

\usepackage[isbn=false,url=false,doi=false,style=alphabetic]{biblatex} 
\addbibresource{sample.bib}

\usepackage{hyperref}

\usepackage{enumitem}
\setlist{itemsep=.5em, parsep = .5em} % < Usually a good idea

\usepackage{amsthm}
\usepackage{amsmath}

\newtheorem{thm}[]{Theorem}
\newtheorem{prop}[thm]{Proposition}
\theoremstyle{definition}
\newtheorem{defn}[]{Definition}

\DeclareMathOperator{\dist}{dist}

\title{Bounds on Coding Theory from Algebraic Geometry}
\author{Guilherme Zeus Dantas e Moura}
%\address{Haverford College}
%\email{gdantasemo@haverford.edu}
%\date{Spring, 2021. Last change in \today}
\date{last compiled \today}

\begin{document}

\begin{abstract}    
    Coding theory is concerned with finding efficient ways to encode a message so that one may correct errors in the message. In algebraic coding theory, we study efficient codes generated from algebraic geometric methods.

    In my paper, I plan on constructing the Reed-Solomon codes, generalizing them using projective curves, and understand the results from \cite{TVZ82} on finding a bound better than the well-known Gilbert--Varshamov bound.
\end{abstract}

\maketitle

\section{Coding theory} \label{s:codingtheory}

\begin{defn}[Code]
    A \emph{code $C$ over an alphabet $A$} is a subset of $A^n = A \times \cdots \times A$.
    We define $n$ as the \emph{length of $C$}.
    A code $C$ over a field $A$ is a \emph{linear code} if $C$ is a vector subspace of $A^n$. An element of a code $C$ is called a \emph{code word}.
\end{defn}

In this paper, $A$ is a finite field unless otherwise stated.

\begin{defn}[Hamming distance]
    We define \emph{Hamming distance} between $\mathbf{x} = (x_1, \dots, x_n), \mathbf{y} = (y_1, \dots, y_n) \in A^n$ as
    \[ \dist(\mathbf{x}, \mathbf{y}) = \#\left( x_i \neq y_i \mid i \in \{1, 2, \dots, n\} \right),\]
    in other words, the number of positions $\mathbf{x}$ and $\mathbf{y}$ differ.
\end{defn}

\begin{prop}
    Hamming distance is a metric over $A^n$, i.e., the following holds for any $\mathbf{x}, \mathbf{y}, \mathbf{z} \in A^n$:
    \begin{itemize}[noitemsep]
        \item $\dist(\mathbf{x}, \mathbf{y}) = 0 \iff \mathbf{x} = \mathbf{y}$;
        \item $\dist(\mathbf{x}, \mathbf{y}) = \dist(\mathbf{x}, \mathbf{y})$;
        \item $\dist(\mathbf{x}, \mathbf{y}) \le \dist(\mathbf{x}, \mathbf{z}) + \dist(\mathbf{z}, \mathbf{y})$.
    \end{itemize}
\end{prop}

\begin{defn}[Parameters of a code]
    If $C$ is a linear code over $A$, we define \emph{dimension of $C$} as $k = \dim_A(C)$ and \emph{minimum distance of $C$} as $d = \min\left\{\dist(\mathbf{x}, \mathbf{y}) \mid \mathbf{x}, \mathbf{y} \in C\right\}$. (\emph{If $C$ is a nonlinear code with length $n$, we can coherently define $k = \log_n{\left|C\right|}$.}) The length $n$, dimension $k$ and minimum distance $d$ are the \emph{parameters} of $C$.
\end{defn}

Suppose Alice wants to send a message to Bob through a channel --- for example, radio waves. They previously agree on a choice of code $C \subset A^n$, with parameters $n, k, d$. Alice will choose one of the $|A|^k$ code words and send it to Bob. Since the channel is not a perfect medium, some positions of the code may change; however, if less than $\frac{d}{2}$ of such changes occur, Bob can take the closest code word to the receiving message using Hamming distance and restore the original message.

Thus, a good code has two properties: it has large $d$ with respect to $n$, in order to correct as many errors as possible; but also has large $k$ with respect to $n$, so that Alice has a wider variety of possible messages to send and send more information.

\begin{defn}
    If $C$ is a code, its code rate is $R = k/n$ and its relative minimum distance is $\delta = d/n$. Note that $R, \delta \in [0, 1]$.
\end{defn}

Therefore, a good code is one with large $R$ --- not much redundancy --- and large $\delta$ --- corrects many errors.

\section{Singleton bound and a promising example} \label{s:singleton}
\begin{thm}[Singleton Bound]
If $C$ is a code with parameters $n, k, d$, then \[k + d \le n + 1,\] or equivalently, \[R + \delta \le 1 + 1/n.\]
\end{thm}
\begin{proof}

\end{proof}

\begin{defn}[Reed--Solomon Codes]

\end{defn}
\begin{prop}
Any Reed--Solomon code meets the Singleton Bound.
\end{prop}
\begin{proof}

\end{proof}
%Explain that Reed--Solomon codes have a limited length compared to the alphabet size.

\section{Generalized Reed-Solomon codes} \label{s:grs}
We shall redefine the Reed--Solomon codes using language related to a projective line. There is a way to replace the ``projective line'' with a ``projective plane curve'' and create other codes, called \emph{Generalized Reed-Solomon codes} or simply \emph{algebraic geometric codes}. We want large $R$ and $\delta$, and these codes yield \begin{equation}\label{eq:g/n} R + \delta \ge 1 + 1/n - g/n,\end{equation} where $n$ is the number of rational points of a curve $X$, with genus $g$.

\section{Final thoughts} \label{s:tvz} On equation \eqref{eq:g/n}, we observe that good algebraic geometric codes are generated by curves with a large ratio between $n$ and $g$. On \cite{TVZ82}, the authors present a sequence of such curves, with $n/g$ large enough to create a better bound than the Gilbert--Varshamov one.

\end{document}

### 2021-04-03 draft/draft.tex
Updates from Overleaf

@@
 \section{Singleton bound and a promising example} \label{s:singleton}
-\begin{thm}[Singleton Bound]
+\begin{thm}[Singleton Bound]\label{thm:singleton_bound}
 If $C$ is a code with parameters $n, k, d$, then \[k + d \le n + 1,\] or equivalently, \[R + \delta \le 1 + 1/n.\]
 \end{thm}
+
+\begin{prop}
+Theorem \ref{thm:singleton_bound} holds for any linear code $C$.
+\end{prop}
+
 \begin{proof}

### 2021-04-03 draft.tex
Local commit
Section 2

--- 2021-04-03 draft/draft.tex
@@
-% !TEX TS-program = pdflatexmk
 \documentclass[11pt, letterpaper]{amsart}
@@
 
+\usepackage[usenames,dvipsnames]{xcolor}
 \usepackage{hyperref}
-
 \usepackage{enumitem}
 \setlist{itemsep=.5em, parsep = .5em} % < Usually a good idea
-
-\usepackage{amsthm}
-\usepackage{amsmath}
 
@@
 
+\usepackage{tcolorbox}
+\tcbuselibrary{most}
+
+\tcolorboxenvironment{thm}{ enhanced jigsaw, colframe=Aquamarine, colback=Aquamarine!8!white, breakable, before skip=5pt plus 10pt minus 3pt, after skip=5pt plus 10pt minus 3pt, grow to left by=8pt, left*=0pt, grow to right by=5pt, right*=0pt, top=0pt, bottom=0pt, sharp corners, rightrule=0pt, toprule=0pt, bottomrule=0pt, leftrule=3pt, parbox=false}
+
+\tcolorboxenvironment{prop}{ enhanced jigsaw, colframe=cyan, colback=cyan!8!white, breakable, before skip=5pt plus 10pt minus 3pt, after skip=5pt plus 10pt minus 3pt, grow to left by=8pt, left*=0pt, grow to right by=5pt, right*=0pt, top=0pt, bottom=0pt, sharp corners, rightrule=0pt, toprule=0pt, bottomrule=0pt, leftrule=3pt, parbox=false}
+
+\tcolorboxenvironment{defn}{ enhanced jigsaw, colframe=OliveGreen, colback=OliveGreen!8!white, breakable, before skip=5pt plus 10pt minus 3pt, after skip=5pt plus 10pt minus 3pt, grow to left by=8pt, left*=0pt, grow to right by=5pt, right*=0pt, top=0pt, bottom=0pt, sharp corners, rightrule=0pt, toprule=0pt, bottomrule=0pt, leftrule=3pt, parbox=false}
+
+\tcolorboxenvironment{proof}{ enhanced jigsaw, colframe=gray, colback=gray!8!white, breakable, before skip=5pt plus 10pt minus 3pt, after skip=5pt plus 10pt minus 3pt, grow to left by=8pt, left*=0pt, grow to right by=5pt, right*=0pt, top=0pt, bottom=0pt, sharp corners, rightrule=0pt, toprule=0pt, bottomrule=0pt, leftrule=3pt, parbox=false}
+
 \DeclareMathOperator{\dist}{dist}
+\DeclareMathOperator{\Ima}{Im}
 
@@
 
+\maketitle
 \begin{abstract}    
@@
 
-    In my paper, I plan on constructing the Reed-Solomon codes, generalizing them using projective curves, and understand the results from \cite{TVZ82} on finding a bound better than the well-known Gilbert--Varshamov bound.
+    In this paper, I will construct the Reed--Solomon codes, generalize them using projective curves, and understand the results from \cite{TVZ82} on finding a bound better than the well-known Gilbert--Varshamov one.
 \end{abstract}
-
-\maketitle
 
@@
 
-Suppose Alice wants to send a message to Bob through a channel --- for example, radio waves.
+Suppose Alice wants to send a message to Bob through a noisy channel.
 They previously agree on a choice of code $C \subset A^n$, with parameters $n, k, d$.
@@
 
+\begin{proof}
+	We will provide the proof for Theorem \ref{thm:singleton_bound} when $C$ is a linear code.
+\end{proof}
+
+\begin{defn}[Reed--Solomon Codes]
+	Let $q$ be a power of a prime, and $\mathbb{F}_q = \{\alpha_1, \alpha_2, \dots, \alpha_q\}$ the field with $q$ elements.
+Let $k$ be an integer, and $\mathcal{L}_k$ the set of all polylomials over $\mathbb{F}_q$ with degree smaller than $k$.
+Let $k \le n \le q$ be an integer.
+The Reed--Solomon code $RS_q(n, k)$ over $\mathbb{F}_q$ is \[
+		RS_q(n, k) = \left\{\left(f(\alpha_1), f(\alpha_2), \dots, f(\alpha_n)\right) \mid f \in \mathcal{L}_k\right\}.
+	\]
+\end{defn}
+
 \begin{prop}
-Theorem \ref{thm:singleton_bound} holds for any linear code $C$.
+	The Reed--Solomon code $R_q(n, k)$ is a linear code with length $n$, dimension $k$ and minimum distance $n - k + 1$.
+	Thus, any Reed--Solomon code meets the inequality of the Singleton Bound.
 \end{prop}
@@
 \begin{proof}
+	$R_q(n, k)$ is a subset of $\mathbb{F}_q^n$, thus it has length $n$.  
+	Note that $\mathcal L_k$ is a vector space over $\mathbb{F}_q$.
+Note that $\{1, x, x^2, \dots, x^{k-1}\}$ is a choice of basis for this vector space, thus it has dimension $k$.
+Consider the map $\phi: \mathcal L_k \to \mathbb{F}_q^n$ given by \[
+		f \mapsto (f(\alpha_1), f(\alpha_2), \dots, f(\alpha_n)).
+	\]
+
+	Note that the map $\phi$ is a linear transformation. Thus, its image $\Ima \phi = RS_q(n, k)$ is also a vector space.  
+	Additionally, if $\phi(f) = \phi(g)$, then $f - g$ has at least $n$ roots, but has degree less than $n$; thus $f - g$ is the zero polylomial, which implies $f = g$.
+Therefore, $\phi$ is also injective.
+This implies that the dimension of the domain $\mathcal L_k$ is the same as the dimension of the image $RS_q(n, k)$, i.e.,  $\dim RS_q(n, k) = k$.
+
+	Finally, consider distinct $f, g \in \mathcal L_k$ and define $d = \dist(\phi(f), \phi(g))$, $f - g$ has at least $n - d$.
+Futhermore, $f - g$ is a non-zero polynomial with degree less than $k$, thus has at most $k - 1$ roots.
+Then,  $ k - 1 \ge \#\ \text{roots} \ge n - d$.
+	Thus, when $d$ is the minimal distance, we get $k + d_{\mathrm{min}} \ge n + 1$, which along the \nameref{thm:singleton_bound} implies \[
+		k + d_\text{min} = n + 1.
+	\]
 
@@
 
-\begin{defn}[Reed--Solomon Codes]
+The Reed--Solomon codes are good codes in the sense that key have the largest possible sum $k + d$ for their length $n$.
+However, Reed--Solomon codes are limited becuase their length is at most the the alphabet size.
 
-\end{defn}
-\begin{prop}
-Any Reed--Solomon code meets the Singleton Bound.
-\end{prop}
-\begin{proof}
-
-\end{proof}
-%Explain that Reed--Solomon codes have a limited length compared to the alphabet size.
-
-\section{Generalized Reed-Solomon codes} \label{s:grs}
+\section{Generalized Reed--Solomon codes} \label{s:grs}
 We shall redefine the Reed--Solomon codes using language related to a projective line.
-There is a way to replace the ``projective line'' with a ``projective plane curve'' and create other codes, called \emph{Generalized Reed-Solomon codes} or simply \emph{algebraic geometric codes}.
+There is a way to replace the ``projective line'' with a ``projective plane curve'' and create other codes, called \emph{Generalized Reed--Solomon codes} or simply \emph{algebraic geometric codes}.
 We want large $R$ and $\delta$, and these codes yield \begin{equation}\label{eq:g/n} R + \delta \ge 1 + 1/n - g/n,\end{equation} where $n$ is the number of rational points of a curve $X$, with genus $g$.

### 2021-04-03 draft.tex
Section 2, again

@@
 
-\tcolorboxenvironment{thm}{ enhanced jigsaw, colframe=Aquamarine, colback=Aquamarine!8!white, breakable, before skip=5pt plus 10pt minus 3pt, after skip=5pt plus 10pt minus 3pt, grow to left by=8pt, left*=0pt, grow to right by=5pt, right*=0pt, top=0pt, bottom=0pt, sharp corners, rightrule=0pt, toprule=0pt, bottomrule=0pt, leftrule=3pt, parbox=false}
+%\tcolorboxenvironment{thm}{ enhanced jigsaw, colframe=Aquamarine, colback=Aquamarine!8!white, breakable, before skip=5pt plus 10pt minus 3pt, after skip=5pt plus 10pt minus 3pt, grow to left by=8pt, left*=0pt, grow to right by=5pt, right*=0pt, top=0pt, bottom=0pt, sharp corners, rightrule=0pt, toprule=0pt, bottomrule=0pt, leftrule=3pt, parbox=false}
 
-\tcolorboxenvironment{prop}{ enhanced jigsaw, colframe=cyan, colback=cyan!8!white, breakable, before skip=5pt plus 10pt minus 3pt, after skip=5pt plus 10pt minus 3pt, grow to left by=8pt, left*=0pt, grow to right by=5pt, right*=0pt, top=0pt, bottom=0pt, sharp corners, rightrule=0pt, toprule=0pt, bottomrule=0pt, leftrule=3pt, parbox=false}
+%\tcolorboxenvironment{prop}{ enhanced jigsaw, colframe=cyan, colback=cyan!8!white, breakable, before skip=5pt plus 10pt minus 3pt, after skip=5pt plus 10pt minus 3pt, grow to left by=8pt, left*=0pt, grow to right by=5pt, right*=0pt, top=0pt, bottom=0pt, sharp corners, rightrule=0pt, toprule=0pt, bottomrule=0pt, leftrule=3pt, parbox=false}
 
-\tcolorboxenvironment{defn}{ enhanced jigsaw, colframe=OliveGreen, colback=OliveGreen!8!white, breakable, before skip=5pt plus 10pt minus 3pt, after skip=5pt plus 10pt minus 3pt, grow to left by=8pt, left*=0pt, grow to right by=5pt, right*=0pt, top=0pt, bottom=0pt, sharp corners, rightrule=0pt, toprule=0pt, bottomrule=0pt, leftrule=3pt, parbox=false}
+%\tcolorboxenvironment{defn}{ enhanced jigsaw, colframe=OliveGreen, colback=OliveGreen!8!white, breakable, before skip=5pt plus 10pt minus 3pt, after skip=5pt plus 10pt minus 3pt, grow to left by=8pt, left*=0pt, grow to right by=5pt, right*=0pt, top=0pt, bottom=0pt, sharp corners, rightrule=0pt, toprule=0pt, bottomrule=0pt, leftrule=3pt, parbox=false}
 
-\tcolorboxenvironment{proof}{ enhanced jigsaw, colframe=gray, colback=gray!8!white, breakable, before skip=5pt plus 10pt minus 3pt, after skip=5pt plus 10pt minus 3pt, grow to left by=8pt, left*=0pt, grow to right by=5pt, right*=0pt, top=0pt, bottom=0pt, sharp corners, rightrule=0pt, toprule=0pt, bottomrule=0pt, leftrule=3pt, parbox=false}
+%\tcolorboxenvironment{proof}{ enhanced jigsaw, colframe=gray, colback=gray!8!white, breakable, before skip=5pt plus 10pt minus 3pt, after skip=5pt plus 10pt minus 3pt, grow to left by=8pt, left*=0pt, grow to right by=5pt, right*=0pt, top=0pt, bottom=0pt, sharp corners, rightrule=0pt, toprule=0pt, bottomrule=0pt, leftrule=3pt, parbox=false}
 
@@
 	We will provide the proof for Theorem \ref{thm:singleton_bound} when $C$ is a linear code.
+
+	WRITE PROOF.
 \end{proof}
@@
 
+\printbibliography
+
 \end{document}

### 2021-04-05 draft.tex
Updating preamble to match Haverford's guideline

--- 2021-04-03 draft.tex
@@
-\documentclass[11pt, letterpaper]{amsart}
-%\usepackage{amsaddr}
+\documentclass[11pt]{amsart}
+\usepackage[letterpaper,left=125pt,right=125pt]{geometry}
 
-\usepackage[isbn=false,url=false,doi=false,style=alphabetic]{biblatex} 
+\usepackage[english]{babel}
+\usepackage{amsmath, amssymb, amsfonts, amsthm, graphicx}
+
+\usepackage[colorlinks,linkcolor=blue,citecolor=blue,urlcolor=blue]{hyperref}
+\usepackage[backend=biber,isbn=false,url=false]{biblatex} 
 \addbibresource{sample.bib}
 
+\theoremstyle{theorem}
+\newtheorem{thm}{Theorem}[section]
+
+\newtheorem{lem}[thm]{Lemma}
+\newtheorem{cor}[thm]{Corollary}
+\newtheorem{prop}[thm]{Proposition}
+\newtheorem{alg}[thm]{Algorithm}
+
+\theoremstyle{definition}
+\newtheorem{defn}[thm]{Definition}
+\newtheorem{conj}[thm]{Conjecture}
+
+\theoremstyle{example}
+\newtheorem{prob}[thm]{Problem}
+
+\theoremstyle{remark}
+\newtheorem{exmp}[thm]{Example}
+\newtheorem{rem}[thm]{Remark}
+\newtheorem{claim}[thm]{Claim}  
+\renewcommand{\theclaim}{}
+
+\numberwithin{equation}{section}
+
 \usepackage[usenames,dvipsnames]{xcolor}
-\usepackage{hyperref}
 \usepackage{enumitem}
-\setlist{itemsep=.5em, parsep = .5em} % < Usually a good idea
-
-\newtheorem{thm}[]{Theorem}
-\newtheorem{prop}[thm]{Proposition}
-\theoremstyle{definition}
-\newtheorem{defn}[]{Definition}
+\setlist{itemsep=.5em, parsep = .5em}
+\usepackage{lipsum}
 
@@
 \DeclareMathOperator{\Ima}{Im}
+\DeclareMathOperator{\dimension}{dim}
 
-\title{Bounds on Coding Theory from Algebraic Geometry}
+\title[Codes from Algebraic Geometry]{Bounds on Coding Theory from Algebraic Geometry}
 \author{Guilherme Zeus Dantas e Moura}
-%\address{Haverford College}
-%\email{gdantasemo@haverford.edu}
-%\date{Spring, 2021. Last change in \today}
-\date{last compiled \today}
+\date{last compiled \today} % <---- Change this date to the format YYYY-MM-DD
 
@@
 \maketitle
-\begin{abstract}    
+\begin{abstract} % NOT REQUIRED
     Coding theory is concerned with finding efficient ways to encode a message so that one may correct errors in the message.
@@
     We define \emph{Hamming distance} between $\mathbf{x} = (x_1, \dots, x_n), \mathbf{y} = (y_1, \dots, y_n) \in A^n$ as
-    \[ \dist(\mathbf{x}, \mathbf{y}) = \#\left( x_i \neq y_i \mid i \in \{1, 2, \dots, n\} \right),\]
+    \begin{equation}
+		\dist(\mathbf{x}, \mathbf{y}) = \#\left( x_i \neq y_i \mid i \in \{1, 2, \dots, n\} \right),
+	\end{equation}
     in other words, the number of positions $\mathbf{x}$ and $\mathbf{y}$ differ.
@@
 \begin{defn}[Parameters of a code]
-    If $C$ is a linear code over $A$, we define \emph{dimension of $C$} as $k = \dim_A(C)$ and \emph{minimum distance of $C$} as $d = \min\left\{\dist(\mathbf{x}, \mathbf{y}) \mid \mathbf{x}, \mathbf{y} \in C\right\}$.
-(\emph{If $C$ is a nonlinear code with length $n$, we can coherently define $k = \log_n{\left|C\right|}$.}) The length $n$, dimension $k$ and minimum distance $d$ are the \emph{parameters} of $C$.
+    If $C$ is a linear code over $A$, we define \emph{dimension of $C$} as $k = \dimension_A(C)$ and \emph{minimum distance of $C$} as $d = \min\left\{\dist(\mathbf{x}, \mathbf{y}) \mid \mathbf{x}, \mathbf{y} \in C\right\}$.
+(\emph{If $C$ is a nonlinear code over an alphabet with size $q$, we can coherently define $k = \log_q{\left|C\right|}$.}) The length $n$, dimension $k$ and minimum distance $d$ are the \emph{parameters} of $C$.
 \end{defn}
@@
 \begin{thm}[Singleton Bound]\label{thm:singleton_bound}
-If $C$ is a code with parameters $n, k, d$, then \[k + d \le n + 1,\] or equivalently, \[R + \delta \le 1 + 1/n.\]
+If $C$ is a code with parameters $n, k, d$, then 
+	\begin{equation}
+		k + d \le n + 1,
+	\end{equation} 
+	or equivalently, 
+	\begin{equation}
+		R + \delta \le 1 + 1/n.
+	\end{equation}
 \end{thm}
@@
 Let $k \le n \le q$ be an integer.
-The Reed--Solomon code $RS_q(n, k)$ over $\mathbb{F}_q$ is \[
+The Reed--Solomon code $RS_q(n, k)$ over $\mathbb{F}_q$ is
+	\begin{equation}
 		RS_q(n, k) = \left\{\left(f(\alpha_1), f(\alpha_2), \dots, f(\alpha_n)\right) \mid f \in \mathcal{L}_k\right\}.
-	\]
+	\end{equation}
 \end{defn}
@@
 Note that $\{1, x, x^2, \dots, x^{k-1}\}$ is a choice of basis for this vector space, thus it has dimension $k$.
-Consider the map $\phi: \mathcal L_k \to \mathbb{F}_q^n$ given by \[
+Consider the map $\phi: \mathcal L_k \to \mathbb{F}_q^n$ given by
+	\begin{equation}
 		f \mapsto (f(\alpha_1), f(\alpha_2), \dots, f(\alpha_n)).
-	\]
+	\end{equation}
 
@@
 Therefore, $\phi$ is also injective.
-This implies that the dimension of the domain $\mathcal L_k$ is the same as the dimension of the image $RS_q(n, k)$, i.e.,  $\dim RS_q(n, k) = k$.
+This implies that the dimension of the domain $\mathcal L_k$ is the same as the dimension of the image $RS_q(n, k)$, i.e.,  $\dimension RS_q(n, k) = k$.
 
-	Finally, consider distinct $f, g \in \mathcal L_k$ and define $d = \dist(\phi(f), \phi(g))$, $f - g$ has at least $n - d$.
+	Finally, consider distinct $f, g \in \mathcal L_k$ and define $d = \dist(\phi(f), \phi(g))$, $f - g$ has at least $n - d$ roots.
 Futhermore, $f - g$ is a non-zero polynomial with degree less than $k$, thus has at most $k - 1$ roots.
 Then,  $ k - 1 \ge \#\ \text{roots} \ge n - d$.
-	Thus, when $d$ is the minimal distance, we get $k + d_{\mathrm{min}} \ge n + 1$, which along the \nameref{thm:singleton_bound} implies \[
+	If we choose $f, g$ such that $d$ is the minimal distance, we get $k + d_{\mathrm{min}} \ge n + 1$, which together with \nameref{thm:singleton_bound} implies 
+	\begin{equation}
 		k + d_\text{min} = n + 1.
-	\]
+	\end{equation}
 
@@
 There is a way to replace the ``projective line'' with a ``projective plane curve'' and create other codes, called \emph{Generalized Reed--Solomon codes} or simply \emph{algebraic geometric codes}.
-We want large $R$ and $\delta$, and these codes yield \begin{equation}\label{eq:g/n} R + \delta \ge 1 + 1/n - g/n,\end{equation} where $n$ is the number of rational points of a curve $X$, with genus $g$.
+We want large $R$ and $\delta$, and these codes yield
+	\begin{equation}
+		\label{eq:g/n} R + \delta \ge 1 + 1/n - g/n,
+	\end{equation}
+	where $n$ is the number of rational points of a curve $X$, with genus $g$.
 

### 2021-04-06 draft.tex
Updating draft

@@
 
-\theoremstyle{theorem}
 \newtheorem{thm}{Theorem}[section]
-
 \newtheorem{lem}[thm]{Lemma}
@@
 \newtheorem{prob}[thm]{Problem}
+\newtheorem{que}[thm]{Question}
 
@@
 \DeclareMathOperator{\dimension}{dim}
+\DeclareMathOperator{\Supp}{Supp}
 
@@
 
+%\begin{abstract} % NOT REQUIRED
+%    Coding theory is concerned with finding efficient ways to encode a message so that one may correct errors in the message.
+In algebraic coding theory, we study efficient codes generated from algebraic geometric methods.
+%    
+%    In this paper, I will construct the Reed--Solomon codes, generalize them using projective curves, and understand the results from \cite{TVZ82} on finding a bound better than the well-known Gilbert--Varshamov one.
+%\end{abstract}
+
 \maketitle
-\begin{abstract} % NOT REQUIRED
-    Coding theory is concerned with finding efficient ways to encode a message so that one may correct errors in the message.
-In algebraic coding theory, we study efficient codes generated from algebraic geometric methods.
-
-    In this paper, I will construct the Reed--Solomon codes, generalize them using projective curves, and understand the results from \cite{TVZ82} on finding a bound better than the well-known Gilbert--Varshamov one.
-\end{abstract}
 
 \section{Coding theory} \label{s:codingtheory}
+
+WRITE INTRODUCTION WITH ALICE AND BOB.
 
@@
 
-\begin{defn}[Reed--Solomon Codes]
+\begin{defn}[Reed--Solomon Codes]\label{defn:rs_codes}
 	Let $q$ be a power of a prime, and $\mathbb{F}_q = \{\alpha_1, \alpha_2, \dots, \alpha_q\}$ the field with $q$ elements.
-Let $k$ be an integer, and $\mathcal{L}_k$ the set of all polylomials over $\mathbb{F}_q$ with degree smaller than $k$.
+Let $k$ be an integer, and ${L}_k$ the set of all polynomials over $\mathbb{F}_q$ with degree smaller than $k$.
 Let $k \le n \le q$ be an integer.
@@
 	\begin{equation}
-		RS_q(n, k) = \left\{\left(f(\alpha_1), f(\alpha_2), \dots, f(\alpha_n)\right) \mid f \in \mathcal{L}_k\right\}.
+		RS_q(n, k) = \left\{\left(f(\alpha_1), f(\alpha_2), \dots, f(\alpha_n)\right) \mid f \in {L}_k\right\}.
 	\end{equation}
@@
 	$R_q(n, k)$ is a subset of $\mathbb{F}_q^n$, thus it has length $n$.  
-	Note that $\mathcal L_k$ is a vector space over $\mathbb{F}_q$.
+	Note that $ L_k$ is a vector space over $\mathbb{F}_q$.
 Note that $\{1, x, x^2, \dots, x^{k-1}\}$ is a choice of basis for this vector space, thus it has dimension $k$.
-Consider the map $\phi: \mathcal L_k \to \mathbb{F}_q^n$ given by
+Consider the map $\phi:  L_k \to \mathbb{F}_q^n$ given by
 	\begin{equation}
@@
 	Note that the map $\phi$ is a linear transformation. Thus, its image $\Ima \phi = RS_q(n, k)$ is also a vector space.  
-	Additionally, if $\phi(f) = \phi(g)$, then $f - g$ has at least $n$ roots, but has degree less than $n$; thus $f - g$ is the zero polylomial, which implies $f = g$.
+	Additionally, if $\phi(f) = \phi(g)$, then $f - g$ has at least $n$ roots, but has degree less than $n$; thus $f - g$ is the zero polynomial, which implies $f = g$.
 Therefore, $\phi$ is also injective.
-This implies that the dimension of the domain $\mathcal L_k$ is the same as the dimension of the image $RS_q(n, k)$, i.e.,  $\dimension RS_q(n, k) = k$.
+This implies that the dimension of the domain $ L_k$ is the same as the dimension of the image $RS_q(n, k)$, i.e.,  $\dimension RS_q(n, k) = k$.
 
-	Finally, consider distinct $f, g \in \mathcal L_k$ and define $d = \dist(\phi(f), \phi(g))$, $f - g$ has at least $n - d$ roots.
-Futhermore, $f - g$ is a non-zero polynomial with degree less than $k$, thus has at most $k - 1$ roots.
+	Finally, consider distinct $f, g \in  L_k$ and define $d = \dist(\phi(f), \phi(g))$, $f - g$ has at least $n - d$ roots.
+Furthermore, $f - g$ is a non-zero polynomial with degree less than $k$, thus has at most $k - 1$ roots.
 Then,  $ k - 1 \ge \#\ \text{roots} \ge n - d$.
@@
 
-The Reed--Solomon codes are good codes in the sense that key have the largest possible sum $k + d$ for their length $n$.
-However, Reed--Solomon codes are limited becuase their length is at most the the alphabet size.
+The Reed--Solomon codes are very good codes in the sense that key have the largest possible sum $k + d$ for their length $n$.
+However, Reed--Solomon codes are limited because their length is at most the alphabet size.
+So, a question naturally arises: Given fixed $\mathbb{F}_q$, are there codes over $\mathbb{F}_q$ with arbitrarily large $n$ and $R + \delta = 1 + 1/n$?
+If not, how large can $R$ and $\delta$ be when $n$ gets larger?
+The Gilbert--Varshamov bound shows that there are codes with
+\begin{equation}
+	1 - R \approx q(\delta), \text{as $n \to \infty$,}
+\end{equation}
+in which
+\begin{equation}
+	q(x) = x \log_q(q-1) - x\log_q(x) - (1-x)\log_q(x).
+\end{equation}
+Are there any better codes?
+
+\section{Rational Functions and Divisors}
+
+\begin{defn}[Rational Function]
+	A rational function $f$	is a function which is the ratio $g/h$ of two polynomials.
+	It is homogeneous if $g, h$ are homogeneous.
+	After cancelling common roots of $g, h$, the roots of $g$ are called \emph{zeros} of $f$ and the roots of $h$ are called the \emph{poles} of $f$.
+\end{defn}
+
+	We say $f$ has order $n$ in $P$ if $P$ is a zero of muliplicity $n$; order $-n$ if $P$ is a pole with multiplicity $n$; order $0$, otherwise.
+
+\begin{defn}[Divisor] 
+	Let $F$ be the algebraic closure of $\mathbb{F}_q$.
+	Let $X$ be an irreducible nonsingular projective curve in $N$-dimensional projective space over $F$.
+	A \emph{divisor} on $X$ is a formal finite sum of the form $D = \sum a_P P$, where $P$ are points of $X$, $a_P$ are integers and $a_P = 0$ for all but finitely many points $P$.
+	The \emph{degree} of $D$ is $\sum n_P$.
+	The \emph{support} $\Supp D$ is the set $\{P \in X : a_P \neq 0\}$
+\end{defn}
+
+If $D = \sum n_p P$, then define the vector space $\mathcal L(D)$ as the set of all homogeneous rational functions $f$ such that the order of $f$ at each point $P$ of $X$ is greater or equal to $n_P$.
+For our study, an important theorem is the following:
+\begin{thm}[Riemman--Roch Theorem, \cite{Wal00}]
+	Let $X$ be a nonsingular projective curve of genus\footnote{For the reader that is not familiar with genus, it is enough to know that it is an integer that can be calculated for any given curve.} $g$ defined over the field $\mathbb{F}_q$ and let $D$ be a divisor on $X$.
+Then
+	\begin{equation}
+		\dim \mathcal L(D) \ge \deg D + 1 - g,
+	\end{equation}
+	with equality holding if $\deg D > 2g - 2$.
+\end{thm}
+
+%Note that, if the degree of $D$ is negative, then
+%\begin{equation}
+%	\mathcal L(D) = \{0\}.
+%\end{equation}
+%Additionally, the \emph{Riemann--Rock theorem} implies that the dimension of the vector space $\mathcal L(D)$ is 
+%\begin{equation}
+%	 \dim\mathcal L(D) \ge \deg D - g + 1,
+%\end{equation}
+%where $g$ denotes the genus of $X$ (for the reader who is not familiar with the term genus, it suffices to know that it is an integer which can be calculated for any given curve).
 
 \section{Generalized Reed--Solomon codes} \label{s:grs}
-We shall redefine the Reed--Solomon codes using language related to a projective line.
-There is a way to replace the ``projective line'' with a ``projective plane curve'' and create other codes, called \emph{Generalized Reed--Solomon codes} or simply \emph{algebraic geometric codes}.
+Let $\mathbb{P}^1(\mathbb{F}_q)$ denote the projective line over $\mathbb{F}$.
+We will write $(a : b)$ to denote the projective point corresponding to the $1$-dimensional vector space through $(a, b)$.
+The points on $\mathbb{P}^1(\mathbb{F}_q)$ are the points
+\begin{equation}
+	P_i = (\alpha_i : 1), \qquad 1 \le i \le q,
+\end{equation}
+and
+\begin{equation}
+	P_\infty = (1 : 0).
+\end{equation}
+
+Following \cite{LS87}, let $\mathcal L_k$ be the set of two-variable homogeneous rational functions which have a pole of order less than $k$ in the point $Q$.
+
+\begin{prop}
+	The sets $\mathcal L_k$ and $L_k$ are mapped with a bijection $\phi: f(x) \mapsto f(x/y)$.
+\end{prop}
+\begin{proof}
+	WRITE PROOF.
+\end{proof}
+
+Then, we can rewrite the Reed--Solomon code from \ref{defn:rs_codes} as
+\begin{equation}
+	RS_q(n, k) = \{f(P_1), f(P_2), \dots, f(P_n) \mid f \in \mathcal L_k\}.
+\end{equation}
+
+\begin{defn}[Algebraic Geometric Code]
+\end{defn}
+
 We want large $R$ and $\delta$, and these codes yield 

### 2021-04-10 draft.tex
Final draft

@@
-\documentclass[11pt]{amsart}
+\documentclass[11pt, oneside]{amsart}
 \usepackage[letterpaper,left=125pt,right=125pt]{geometry}
@@
 \usepackage{amsmath, amssymb, amsfonts, amsthm, graphicx}
+\usepackage[mathscr]{eucal}
 
@@
 \newtheorem{prop}[thm]{Proposition}
-\newtheorem{alg}[thm]{Algorithm}
 
@@
 \newtheorem{defn}[thm]{Definition}
-\newtheorem{conj}[thm]{Conjecture}
-
-\theoremstyle{example}
-\newtheorem{prob}[thm]{Problem}
-\newtheorem{que}[thm]{Question}
 
 \theoremstyle{remark}
-\newtheorem{exmp}[thm]{Example}
 \newtheorem{rem}[thm]{Remark}
-\newtheorem{claim}[thm]{Claim}  
-\renewcommand{\theclaim}{}
 
@@
 
-\title[Codes from Algebraic Geometry]{Bounds on Coding Theory from Algebraic Geometry}
+\usepackage{todonotes}
+\setuptodonotes{size=\tiny, linecolor=black, backgroundcolor=yellow!30}
+
+\usepackage{makecell}
+
+\title[Draft: Codes from Algebraic Geometry]{Draft: Bounds on Coding Theory\\from Algebraic Geometry}
 \author{Guilherme Zeus Dantas e Moura}
-\date{last compiled \today} % <---- Change this date to the format YYYY-MM-DD
+\date{2021-04-09} % <---- Change this date to the format YYYY-MM-DD
 
@@
 %	Coding theory is concerned with finding efficient ways to encode a message so that one may correct errors in the message.
-In algebraic coding theory, we study efficient codes generated from algebraic geometric methods.
+%	In algebraic coding theory, we study efficient codes generated from algebraic geometric methods.
 %    
@@
 
-WRITE INTRODUCTION WITH ALICE AND BOB.
+Suppose Alice wants to send a message to Bob though a noisy channel.
+When Bob receives the message, it is possible that some of the information is misinterpreted.
+For example, if Alice sends the message `\texttt{food}' through the noisy channel, one of its letters may be misinterpreted and Bob could actually receive `\texttt{\underline{m}ood}'.
+So, the question Coding Theory tries to answer is:
+How can Alice and Bob agree on a system beforehand so that, if Alice sends a message to Bob, even if some misinterpretations occur, Bob will be able to understand the correct meaning?
 
-\begin{defn}[Code]
+\begin{defn}[Code] \label{defn:code}
     A \emph{code $C$ over an alphabet $A$} is a subset of $A^n = A \times \cdots \times A$.
     We define $n$ as the \emph{length of $C$}.
-    A code $C$ over a field $A$ is a \emph{linear code} if $C$ is a vector subspace of $A^n$. An element of a code $C$ is called a \emph{code word}.
+	An element of a code $C$ is called a \emph{code word}.
+	A code $C$ over a finite field $\mathbb{F}_q$ is a \emph{linear code} if $C$ is a vector subspace of $\mathbb{F}_q^n$.
 \end{defn}
 
-In this paper, $A$ is a finite field unless otherwise stated.
+Back to the analogy with Alice and Bob, the code $C$ is the set of all the messages that Alice may send to Bob, according to their agreement.
 
-\begin{defn}[Hamming distance]
+\begin{defn}[Hamming distance] \label{defn:hamming}
     We define \emph{Hamming distance} between $\mathbf{x} = (x_1, \dots, x_n), \mathbf{y} = (y_1, \dots, y_n) \in A^n$ as
     \begin{equation}
-		\dist(\mathbf{x}, \mathbf{y}) = \#\left( x_i \neq y_i \mid i \in \{1, 2, \dots, n\} \right),
+		\dist(\mathbf{x}, \mathbf{y}) = \#\left(i \in \{1, 2, \dots, n\} \mid x_i \neq y_i\right),
 	\end{equation}
@@
 
-\begin{prop}
+\begin{prop} \label{prop:hamming}
     Hamming distance is a metric over $A^n$, i.e., the following holds for any $\mathbf{x}, \mathbf{y}, \mathbf{z} \in A^n$:
@@
     If $C$ is a linear code over $A$, we define \emph{dimension of $C$} as $k = \dimension_A(C)$ and \emph{minimum distance of $C$} as $d = \min\left\{\dist(\mathbf{x}, \mathbf{y}) \mid \mathbf{x}, \mathbf{y} \in C\right\}$.
-(\emph{If $C$ is a nonlinear code over an alphabet with size $q$, we can coherently define $k = \log_q{\left|C\right|}$.}) The length $n$, dimension $k$ and minimum distance $d$ are the \emph{parameters} of $C$.
+	(\emph{If $C$ is a nonlinear code over an alphabet with size $q$, we can coherently define $k = \log_q{\left|C\right|}$.})
+	The length $n$, dimension $k$ and minimum distance $d$ are the \emph{parameters} of $C$.
 \end{defn}
 
-Suppose Alice wants to send a message to Bob through a noisy channel.
-They previously agree on a choice of code $C \subset A^n$, with parameters $n, k, d$.
-Alice will choose one of the $|A|^k$ code words and send it to Bob.
-Since the channel is not a perfect medium, some positions of the code may change; however, if less than $\frac{d}{2}$ of such changes occur, Bob can take the closest code word to the receiving message using Hamming distance and restore the original message.
+Alice and Bob agree on a choice of code $C \subset A^n$, with parameters $n, k, d$.
+To send a message, Alice will choose one of the $|A|^k$ code words and send it to Bob.
+Since the channel is not a perfect medium, some positions of the code may change;
+however, if less than $\frac{d}{2}$ of such changes occur, Bob can take the closest code word to the receiving message using Hamming distance and restore the original message.
 
-Thus, a good code has two properties: it has large $d$ with respect to $n$, in order to correct as many errors as possible; but also has large $k$ with respect to $n$, so that Alice has a wider variety of possible messages to send and send more information.
+Thus, a good code has two properties: it has large $d$ with respect to $n$, in order to correct as many errors as possible;
+but also has large $k$ with respect to $n$, so that Alice has a wider variety of possible messages to send and send more information.
 
 \begin{defn}
-    If $C$ is a code, its code rate is $R = k/n$ and its relative minimum distance is $\delta = d/n$. Note that $R, \delta \in [0, 1]$.
+	If $C$ is a code, its \emph{code rate} is $R = k/n$ and its \emph{relative minimum distance} is $\delta = d/n$.
+	Note that $R, \delta \in [0, 1]$.
 \end{defn}
@@
 \begin{proof}
-	We will provide the proof for Theorem \ref{thm:singleton_bound} when $C$ is a linear code.
-
-	WRITE PROOF.
+	We will provide the proof for Theorem \ref{thm:singleton_bound} when $C$ is a linear code.\todo{Write proof}
 \end{proof}
 
-\begin{defn}[Reed--Solomon Codes]\label{defn:rs_codes}
+\begin{defn}[Reed--Solomon codes, \cite{LS87}]\label{defn:rs_codes}
 	Let $q$ be a power of a prime, and $\mathbb{F}_q = \{\alpha_1, \alpha_2, \dots, \alpha_q\}$ the field with $q$ elements.
 	Let $k$ be an integer, and ${L}_k$ the set of all polynomials over $\mathbb{F}_q$ with degree smaller than $k$.
-Let $k \le n \le q$ be an integer.
-The Reed--Solomon code $RS_q(n, k)$ over $\mathbb{F}_q$ is
+	Let $k \le n \le q$ be an integer. The Reed--Solomon code $RS_q(n, k)$ over $\mathbb{F}_q$ is 
 	\begin{equation}
@@
 \begin{prop}
-	The Reed--Solomon code $R_q(n, k)$ is a linear code with length $n$, dimension $k$ and minimum distance $n - k + 1$.
+	The Reed--Solomon code $RS_q(n, k)$ is a linear code with length $n$, dimension $k$ and minimum distance $n - k + 1$.
 	Thus, any Reed--Solomon code meets the inequality of the Singleton Bound.
@@
 \begin{proof}
-	$R_q(n, k)$ is a subset of $\mathbb{F}_q^n$, thus it has length $n$.  
+	$RS_q(n, k)$ is a subset of $\mathbb{F}_q^n$, thus it has length $n$.  
 	Note that $ L_k$ is a vector space over $\mathbb{F}_q$.
@@
 
-	Note that the map $\phi$ is a linear transformation. Thus, its image $\Ima \phi = RS_q(n, k)$ is also a vector space.  
+	Note that the map $\phi$ is a linear transformation.
+	Thus, its image $\Ima \phi = RS_q(n, k)$ is also a vector space.  
 	Additionally, if $\phi(f) = \phi(g)$, then $f - g$ has at least $n$ roots, but has degree less than $n$; thus $f - g$ is the zero polynomial, which implies $f = g$.
@@
 If not, how large can $R$ and $\delta$ be when $n$ gets larger?
-The Gilbert--Varshamov bound shows that there are codes with
+The well-known Gilbert--Varshamov bound shows that there are codes with 
 \begin{equation}
-	1 - R \approx q(\delta), \text{as $n \to \infty$,}
+	1 - R \approx H_q(\delta), \text{ as $n \to \infty$,}
 \end{equation}
@@
 \begin{equation}
-	q(x) = x \log_q(q-1) - x\log_q(x) - (1-x)\log_q(x).
+	H_q(x) = x \log_q(q-1) - x\log_q(x) - (1-x)\log_q(x).
 \end{equation}
-Are there any better codes?
+The article \cite{TVZ82} uses Algebraic Geometry to show that there are codes that give better bounds.
 
-\section{Rational Functions and Divisors}
+\section{Curves, Rational Functions and Divisors}
 
-\begin{defn}[Rational Function]
-	A rational function $f$	is a function which is the ratio $g/h$ of two polynomials.
-	It is homogeneous if $g, h$ are homogeneous.
-	After cancelling common roots of $g, h$, the roots of $g$ are called \emph{zeros} of $f$ and the roots of $h$ are called the \emph{poles} of $f$.
+Through this section, let $K$ be a field and $L$ its algebraic closure.
+
+\begin{defn}[Algebraic curves]
+	An affine algebraic plane curve $\mathfrak C_f$ is the zero set of a polynomial $f \in K[x, y]$.
+	A projective algebraic plane curve $\mathfrak C_F$ is the zero set in a projective plane of a homogeneous polynomial $F \in K[X, Y, Z]$.
+	Generally, algebraic curves are algebraic varieties of dimension $1$.
 \end{defn}
 
-	We say $f$ has order $n$ in $P$ if $P$ is a zero of muliplicity $n$; order $-n$ if $P$ is a pole with multiplicity $n$; order $0$, otherwise.
+Note that there exists a bijection, called \emph{homogenization}, between the polynomials in $K[x, y]$ and the homogeneous polynomials in $K[X, Y, Z]$ defined by $f(x, y) \mapsto Z^{\deg f}f(X/Z, Y/Z)$.
+Because of this, we'll denote by $\mathfrak C$ both $\mathfrak C_f$ and $\mathfrak C_F$, where the usage is clear by context.
+
+\begin{defn}[Rational points, \cite{Wal00}] %Not word-by-word
+	Let $\mathfrak C$ be a projective curve defined by $F(X, Y, Z) = 0$, where $F \in K[X, Y, Z]$ is homogeneous polynomial.
+	A point $(X_0 : Y_0 : Z_0) \in \mathbb{P}^2(L)$ is called a \emph{$L$-rational point} on $\mathfrak C$ if $F(X_0, Y_0, Z_0) = 0$.
+	Additionally, if $(X_0 : Y_0 : Z_0)$ is also in $\mathbb{P}^2(K)$, we call it simply a \emph{rational point} on $\mathfrak C$.
+\end{defn}
+
+\begin{thm}[Bezout's theorem, \cite{Wal00}] %Not word-by-word
+	If $F, G \in K[X, Y, Z]$ are homogeneous polynomials of degrees $d$ and $e$, respectively, then their curves $\mathfrak C_F$ and $\mathfrak C_G$ intersect in exactly $de$ $L$-rational points, counting multiplicity.
+\end{thm}
+
+\begin{defn}[Rational function]
+	A rational function $f$ over a $K$ is the ratio $g/h$ of polynomials $g, h \in K[x, y]$.
+	A homogeneous rational function $F$ over a $K$ is the ratio $G/H$ of homogeneous polynomials $G, H \in K[x, y]$.
+
+	After cancelling common roots of $g, h$, the roots of $g$ are called \emph{zeros} of $f$ and the roots of $h$ are called the \emph{poles} of $f$.
+
+	We say $f$ has order $n$ in $P$ if $P$ is a zero of multiplicity $n$; order $-n$ if $P$ is a pole with multiplicity $n$; and order $0$, otherwise.
+\end{defn}
 
 \begin{defn}[Divisor] 
-	Let $F$ be the algebraic closure of $\mathbb{F}_q$.
-	Let $X$ be an irreducible nonsingular projective curve in $N$-dimensional projective space over $F$.
-	A \emph{divisor} on $X$ is a formal finite sum of the form $D = \sum a_P P$, where $P$ are points of $X$, $a_P$ are integers and $a_P = 0$ for all but finitely many points $P$.
+	Let $\overline{\mathbb{F}_q}$ be the algebraic closure of $\mathbb{F}_q$.
+	Let $\mathfrak C$ be a projective plane curve defined over $\mathbb{F}_q$.
+	A \emph{divisor} $D$ on $\mathfrak C$ is a formal finite sum of the form $D = \sum a_P P$, where $P$ are points of $\mathfrak C$, $a_P$ are integers and $a_P = 0$ for all but finitely many points $P$.
 	The \emph{degree} of $D$ is $\sum n_P$.
-	The \emph{support} $\Supp D$ is the set $\{P \in X : a_P \neq 0\}$
+	The \emph{support} $\Supp D$ is the set $\{P \in X : a_P \neq 0\}$.
 \end{defn}
 
-If $D = \sum n_p P$, then define the vector space $\mathcal L(D)$ as the set of all homogeneous rational functions $f$ such that the order of $f$ at each point $P$ of $X$ is greater or equal to $n_P$.
+\begin{defn}[Field of rational functions on a curve, \cite{Wal00}] %Copied
+	Let $F$ be the polynomial which defines the nonsingular projective plane curve $C$ over the field $\mathbb{F}_q$. The \emph{field of rational functions on $C$} is
+	\begin{equation}
+		\mathbb{F}_q(C) := \left(\left\{\frac{G}{H}\, \bigg|\,\, \makecell{G, H \in \mathbb{F}_q[X, Y, Z]\\\text{are homogeneous}\\\text{of the same degree}} \right\} \cup \{0\}\right) / \sim
+	\end{equation}
+	where $g/h \sim g'/h'$ if, and only if, $gh' - g'h \in \langle F \rangle \subset \mathbb{F}_q[X, Y, Z]$.
+	\todo{Redefine it in a way that actually shows it is pretty simple.}
+\end{defn}
+
+\begin{defn}[\cite{LS87}]
+	If $D = \sum n_p P$, then define the vector space $\mathcal L(D)$ as the set of all homogeneous rational functions $f$ such that the order of $f$ at each point $P$ of $\mathfrak C$ is greater or equal to $-n_P$.
+\end{defn}
+
 For our study, an important theorem is the following:
 \begin{thm}[Riemman--Roch Theorem, \cite{Wal00}]
-	Let $X$ be a nonsingular projective curve of genus\footnote{For the reader that is not familiar with genus, it is enough to know that it is an integer that can be calculated for any given curve.} $g$ defined over the field $\mathbb{F}_q$ and let $D$ be a divisor on $X$.
+	Let $\mathfrak C$ be a nonsingular projective curve of genus%
+	\footnote{For the reader that is not familiar with genus, it is enough to know that it is an integer that can be calculated for any given curve.}
+	$g$ defined over the field $\mathbb{F}_q$ and let $D$ be a divisor on $\mathfrak C$.
 	Then
@@
 %\end{equation}
-%where $g$ denotes the genus of $X$ (for the reader who is not familiar with the term genus, it suffices to know that it is an integer which can be calculated for any given curve).
+%where $g$ denotes the genus of $\mathfrak C$ (for the reader who is not familiar with the term genus, it suffices to know that it is an integer which can be calculated for any given curve).
 
 \section{Generalized Reed--Solomon codes} \label{s:grs}
-Let $\mathbb{P}^1(\mathbb{F}_q)$ denote the projective line over $\mathbb{F}$.
+Let $\mathbb{P}^1(\mathbb{F}_q)$ denote the projective line over $\mathbb{F}_q$.
 We will write $(a : b)$ to denote the projective point corresponding to the $1$-dimensional vector space through $(a, b)$.
@@
 \begin{equation}
-	P_i = (\alpha_i : 1), \qquad 1 \le i \le q,
-\end{equation}
-and
-\begin{equation}
+	P_i = (\alpha_i : 1), \quad 1 \le i \le q, \qquad \text{and} \qquad 
 	P_\infty = (1 : 0).
@@
 
-Following \cite{LS87}, let $\mathcal L_k$ be the set of two-variable homogeneous rational functions which have a pole of order less than $k$ in the point $Q$.
+Consider the divisor $D = (k-1)P_\infty$ and the associated vector space $\mathcal L(D)$, which can be seen as the set of two-variable homogeneous rational functions which have a pole of order less than $k$ in the point $P_\infty$.
 
 \begin{prop}
-	The sets $\mathcal L_k$ and $L_k$ are mapped with a bijection $\phi: f(x) \mapsto f(x/y)$.
+	The sets $L_k$ and $\mathcal L(D)$ are mapped with a bijection (homogenization) $\phi: f(x) \mapsto Y^{\deg f} f(X/Y)$.
 \end{prop}
 \begin{proof}
-	WRITE PROOF.
+	\todo{Write proof.}
 \end{proof}
 
-Then, we can rewrite the Reed--Solomon code from \ref{defn:rs_codes} as
+Then, we can rewrite the Reed--Solomon code from Definition \ref{defn:rs_codes} as
 \begin{equation}
-	RS_q(n, k) = \{f(P_1), f(P_2), \dots, f(P_n) \mid f \in \mathcal L_k\}.
+	RS_q(n, k) = \{f(P_1), f(P_2), \dots, f(P_n) \mid f \in \mathcal L(D)\}.
 \end{equation}
 
-\begin{defn}[Algebraic Geometric Code]
+Here, we are evaluating the function $f$ in the points of the projective line.
+We shall generalize the idea by changing the projective line to an arbitrary projective curve, and allowing other divisors $D$.
+
+\begin{defn}[Algebraic geometric codes, \cite{LS87, Wal00}] %Copied from Wal00
+	Let $\mathfrak C$ be an irreducible nonsingular%
+	\todo{Provide an explanation for why the `irreducible nonsingular' is there, but not a thing that the reader should worry. I think the key is some sort of multiplicity.}
+	projective plane curve, let $D$ be a divisor on $\mathfrak C$ and let $\mathcal P = \{P_1, P_2, \dots, P_n\}$ be a set of rational points on $\mathfrak C$.
+	Assume $\mathcal P$ and $\Supp D$ have no points in common, thus, no $P_i$ can be a pole of any $f \in \mathcal L(D)$, and $f(P_i)$ is well-defined for any $f \in \mathcal L(D)$ and any $P_i \in \mathcal P$.
+	Then, the \emph{algebraic geometric code} associated to $\mathfrak C, \mathcal P$ and $D$ is
+	\begin{equation}
+		C(\mathfrak C, \mathcal P, D) := \{(f(P_1), \dots, f(P_n)) \mid f \in L(D)\} \subset \mathbb{F}_q^n.
+	\end{equation}
 \end{defn}
+
+\begin{thm}[\cite{Wal00}]
+	Let $\mathfrak C, \mathcal P, D$ be as above.
+Let $g$ denote the genus of $\mathfrak C$.
+Suppose $D$ satisfies $2g - 2 < \deg D < n$.
+Then the algebraic geometric code $C(\mathfrak C, \mathcal P, D)$ is linear of:
+	\begin{enumerate}[label = \textbullet, itemsep = 0pt]
+		\item length $n$,
+		\item dimension $\deg D + 1 - g$,
+		\item minimum distance $d \ge n - \deg D$.
+	\end{enumerate}
+\end{thm}
+
+\begin{proof}
+	\todo{Write proof.}
+\end{proof}
 
@@
 	\end{equation}
-where $n$ is the number of rational points of a curve $X$, with genus $g$.
+where $n$ is the number of rational points of a curve $\mathfrak C$, with genus $g$; this is an interesting result!
+All the work done can be applied for algebraic curves in higher dimensional projective spaces.
 
-\section{Final thoughts} \label{s:tvz} On equation \eqref{eq:g/n}, we observe that good algebraic geometric codes are generated by curves with a large ratio between $n$ and $g$.
-On \cite{TVZ82}, the authors present a sequence of such curves, with $n/g$ large enough to create a better bound than the Gilbert--Varshamov one.
+\section{Final thoughts}\label{s:tvz}
+
+On equation \eqref{eq:g/n}, we observe that good algebraic geometric codes are generated by curves with a small ratio between $g$ and $n$.
+On \cite{TVZ82},\todo{Talk a bit more about it.} the authors present a sequence of such curves, with $g/n$ large enough to create a better bound than the Gilbert--Varshamov one.
 

### 2021-05-01 draft.tex
2021.05.01 update

@@
 \newtheorem{rem}[thm]{Remark}
+\newtheorem*{exmp*}{Example}
 
@@
 
-\title[Draft: Codes from Algebraic Geometry]{Draft: Bounds on Coding Theory\\from Algebraic Geometry}
+\title[Codes from Algebraic Geometry]{Bounds on Coding Theory\\from Algebraic Geometry}
 \author{Guilherme Zeus Dantas e Moura}
-\date{2021-04-09} % <---- Change this date to the format YYYY-MM-DD
+\date{2021-05-07} % <---- Change this date to the format YYYY-MM-DD
 
@@
         \item $\dist(\mathbf{x}, \mathbf{y}) = 0 \iff \mathbf{x} = \mathbf{y}$;
-        \item $\dist(\mathbf{x}, \mathbf{y}) = \dist(\mathbf{x}, \mathbf{y})$;
+        \item $\dist(\mathbf{x}, \mathbf{y}) = \dist(\mathbf{y}, \mathbf{z})$;
         \item $\dist(\mathbf{x}, \mathbf{y}) \le \dist(\mathbf{x}, \mathbf{z}) + \dist(\mathbf{z}, \mathbf{y})$.
@@
 \begin{defn}[Parameters of a code]
-    If $C$ is a linear code over $A$, we define \emph{dimension of $C$} as $k = \dimension_A(C)$ and \emph{minimum distance of $C$} as $d = \min\left\{\dist(\mathbf{x}, \mathbf{y}) \mid \mathbf{x}, \mathbf{y} \in C\right\}$.
-	(\emph{If $C$ is a nonlinear code over an alphabet with size $q$, we can coherently define $k = \log_q{\left|C\right|}$.})
+	If $C$ is a code over $A$, we define \emph{dimension of $C$} as $k = \log_{|A|}|C|$ and \emph{minimum distance of $C$} as $d = \min\left\{\dist(\mathbf{x}, \mathbf{y}) \mid \mathbf{x} \neq \mathbf{y} \in C\right\}$.
+	(\emph{If $C$ is a linear code, the definition above is equivalent to $k = \dimension_{A}(C)$.})
 	The length $n$, dimension $k$ and minimum distance $d$ are the \emph{parameters} of $C$.
@@
 If $C$ is a code with parameters $n, k, d$, then 
-	\begin{equation}
+	\begin{equation} % IF SPACE NEEDED, TRANSFORM THESE EQUATIONS INTO INLINE
 		k + d \le n + 1,
@@
 
+We will provide the proof for Theorem \ref{thm:singleton_bound} when $C$ is a linear code over a field $K$.
+
 \begin{proof}
-	We will provide the proof for Theorem \ref{thm:singleton_bound} when $C$ is a linear code.\todo{Write proof}
+	Let $W := \{\mathbf{x} = (x_1, \dots, x_n) \mid x_{d} = \dots = x_n = 0\}$, which is a vector subspace of $K^n$ with dimension $d - 1$.
+Since $C$ is a vector space, $\vec 0 \in C$.
+For any non-zero vector $\vec v \in C$, $\dist(\vec 0, \vec v) \ge d$, thus $\vec v$ has at least $d$ non-zero entries, and therefore $\vec v \notin W$.
+Thus, $W \cap C = \{\vec 0\}$.
+
+	Let $\vec w_1, \dots, \vec w_{d-1}$ and $\vec v_1, \dots, \vec v_k$ be a choice of basis for $W$ and $C$, respectively.
+Since $W \cap C = \{\vec 0\}$, the vectors $\vec w_1, \dots, \vec w_{d-1}, \vec v_1, \dots, \vec v_k$ are linearly independent.
+They all are vectors in $K^n$, therefore, $k + d - 1 \le n$.
 \end{proof}
@@
 
-The Reed--Solomon codes are very good codes in the sense that key have the largest possible sum $k + d$ for their length $n$.
+The Reed--Solomon codes are very good codes in the sense that they have the largest possible sum $k + d$ for their length $n$.
 However, Reed--Solomon codes are limited because their length is at most the alphabet size.
@@
 
-\begin{defn}[Algebraic curves]
+\begin{defn}[Algebraic plane curves]
 	An affine algebraic plane curve $\mathfrak C_f$ is the zero set of a polynomial $f \in K[x, y]$.
-	A projective algebraic plane curve $\mathfrak C_F$ is the zero set in a projective plane of a homogeneous polynomial $F \in K[X, Y, Z]$.
-	Generally, algebraic curves are algebraic varieties of dimension $1$.
+	A projective algebraic plane curve $\mathfrak C_F$ is the zero set in a projective plane of a homogeneous polynomial $F \in K[X, Y, Z]$.\footnote{In more general terms, algebraic curves (as opposed to algebraic plane curves) are algebraic varieties of dimension $1$.
+For this paper, we will not worry about this; our discussion will be based on algebraic plane curves, but the results also follow in higher dimensions.}
 \end{defn}
@@
 \begin{defn}[Rational points, \cite{Wal00}] %Not word-by-word
-	Let $\mathfrak C$ be a projective curve defined by $F(X, Y, Z) = 0$, where $F \in K[X, Y, Z]$ is homogeneous polynomial.
+	Let $\mathfrak C$ be a projective curve defined by $F(X, Y, Z) = 0$, where $F \in K[X, Y, Z]$ is a homogeneous polynomial.
 	A point $(X_0 : Y_0 : Z_0) \in \mathbb{P}^2(L)$ is called a \emph{$L$-rational point} on $\mathfrak C$ if $F(X_0, Y_0, Z_0) = 0$.
@@
 
+\begin{exmp*}
+	Consider the curve $\mathfrak C$ defined by $X^2 + Y^2 + Z^2 = 0$ over $\mathbb{F}_7$.
+	The point $(1 : 2 : 3)$ is a rational point on $\mathfrak C$.
+	Note that the polynomial $x^2 - 3$ is irreducible over $\mathbb{F}_7$, but there it has a root $\alpha$ in its algebraic closure, $\overline{\mathbb{F}_7}$.
+The projective point $(1 :  \alpha : \alpha)$ is a $\overline{\mathbb{F}_7}$-rational point.
+\end{exmp*}
+
 \begin{thm}[Bezout's theorem, \cite{Wal00}] %Not word-by-word
-	If $F, G \in K[X, Y, Z]$ are homogeneous polynomials of degrees $d$ and $e$, respectively, then their curves $\mathfrak C_F$ and $\mathfrak C_G$ intersect in exactly $de$ $L$-rational points, counting multiplicity.
+	If $F, G \in K[X, Y, Z]$ are homogeneous polynomials of degrees $d$ and $e$, respectively, then their curves $\mathfrak C_F$ and $\mathfrak C_G$ intersect in exactly $d\cdot e$ $L$-rational points, counting multiplicity.
 \end{thm}
@@
 \begin{defn}[Rational function]
-	A rational function $f$ over a $K$ is the ratio $g/h$ of polynomials $g, h \in K[x, y]$.
+	A rational function $f$ over $K$ is the ratio $g/h$ of polynomials $g, h \in K[x, y]$.
 	A homogeneous rational function $F$ over a $K$ is the ratio $G/H$ of homogeneous polynomials $G, H \in K[x, y]$.
@@
 	After cancelling common roots of $g, h$, the roots of $g$ are called \emph{zeros} of $f$ and the roots of $h$ are called the \emph{poles} of $f$.  
-
-	We say $f$ has order $n$ in $P$ if $P$ is a zero of multiplicity $n$; order $-n$ if $P$ is a pole with multiplicity $n$; and order $0$, otherwise.
+	We say $f$ has order $n$ at $P$ if $P$ is a zero of multiplicity $n$; order $-n$ if $P$ is a pole with multiplicity $n$; and order $0$, otherwise.
 \end{defn}
@@
 \begin{defn}[Divisor] 
-	Let $\overline{\mathbb{F}_q}$ be the algebraic closure of $\mathbb{F}_q$.
-	Let $\mathfrak C$ be a projective plane curve defined over $\mathbb{F}_q$.
-	A \emph{divisor} $D$ on $\mathfrak C$ is a formal finite sum of the form $D = \sum a_P P$, where $P$ are points of $\mathfrak C$, $a_P$ are integers and $a_P = 0$ for all but finitely many points $P$.
-	The \emph{degree} of $D$ is $\sum n_P$.
+%	Let $\overline{\mathbb{F}_q}$ be the algebraic closure of $\mathbb{F}_q$.
+%	Let $\mathfrak C$ be a projective plane curve defined over $\mathbb{F}_q$.
+	Let $\mathfrak C$ be a projective plane curve defined over $K$.
+	A \emph{divisor} $D$ on $\mathfrak C$ is a formal finite sum of the form $D = \sum a_P P$, where $P$ varies over the $L$-rational points on $\mathfrak C$, $a_P$ is an integer and $a_P = 0$ for all but finitely many points $P$.
+	The \emph{degree} of $D$ is $\sum a_P$.
 	The \emph{support} $\Supp D$ is the set $\{P \in X : a_P \neq 0\}$.
@@
 	Let $\mathfrak C$ be an irreducible nonsingular%
-	\todo{Provide an explanation for why the `irreducible nonsingular' is there, but not a thing that the reader should worry. I think the key is some sort of multiplicity.}
+	\footnote{The adjectives make sure $\mathfrak C$ is well-behaved. The reader should not worry about them.}
+%%	\todo{Provide an explanation for why the `irreducible nonsingular' is there, but not a thing that the reader should worry. I think the key is some sort of multiplicity.}
 	projective plane curve, let $D$ be a divisor on $\mathfrak C$ and let $\mathcal P = \{P_1, P_2, \dots, P_n\}$ be a set of rational points on $\mathfrak C$.

### 2021-05-03 draft.tex
05-03 Update - Starbucks Edition

@@
         \item $\dist(\mathbf{x}, \mathbf{y}) = 0 \iff \mathbf{x} = \mathbf{y}$;
-        \item $\dist(\mathbf{x}, \mathbf{y}) = \dist(\mathbf{y}, \mathbf{z})$;
+        \item $\dist(\mathbf{x}, \mathbf{y}) = \dist(\mathbf{y}, \mathbf{x})$;
         \item $\dist(\mathbf{x}, \mathbf{y}) \le \dist(\mathbf{x}, \mathbf{z}) + \dist(\mathbf{z}, \mathbf{y})$.
@@
 \end{prop}
+
+The proof of Proposition \ref{prop:hamming} is ommited from this short paper.
 
@@
 	Then,  $ k - 1 \ge \#\ \text{roots} \ge n - d$.
-	If we choose $f, g$ such that $d$ is the minimal distance, we get $k + d_{\mathrm{min}} \ge n + 1$, which together with \nameref{thm:singleton_bound} implies 
-	\begin{equation}
-		k + d_\text{min} = n + 1.
-	\end{equation}
-
+	If we choose $f, g$ such that $d$ is the minimal distance, we get $k + d_{\mathrm{min}} \ge n + 1$, which together with \nameref{thm:singleton_bound} implies $k + d_\text{min} = n + 1$.
 \end{proof}
@@
 
-Note that there exists a bijection, called \emph{homogenization}, between the polynomials in $K[x, y]$ and the homogeneous polynomials in $K[X, Y, Z]$ defined by $f(x, y) \mapsto Z^{\deg f}f(X/Z, Y/Z)$.
+Note that there exists a natural injection, called \emph{homogenization}, from the set of polynomials in $K[x, y]$ and the set of homogeneous polynomials in $K[X, Y, Z]$ defined by $f(x, y) \mapsto Z^{\deg f}f(X/Z, Y/Z)$.
 Because of this, we'll denote by $\mathfrak C$ both $\mathfrak C_f$ and $\mathfrak C_F$, where the usage is clear by context.
@@
 	A point $(X_0 : Y_0 : Z_0) \in \mathbb{P}^2(L)$ is called a \emph{$L$-rational point} on $\mathfrak C$ if $F(X_0, Y_0, Z_0) = 0$.
-	Additionally, if $(X_0 : Y_0 : Z_0)$ is also in $\mathbb{P}^2(K)$, we call it simply a \emph{rational point} on $\mathfrak C$.
+	Additionally, if $(X_0 : Y_0 : Z_0)$ is also in $\mathbb{P}^2(K)$, we call it a \emph{$K$-rational point} on $\mathfrak C$, or simply a \emph{rational point} on $\mathfrak C$.
 \end{defn}
@@
 	Consider the curve $\mathfrak C$ defined by $X^2 + Y^2 + Z^2 = 0$ over $\mathbb{F}_7$.
-	The point $(1 : 2 : 3)$ is a rational point on $\mathfrak C$.
+	The point $(1 : 2 : 3)$ is a $\mathbb{F}_7$-rational point on $\mathfrak C$.
 	Note that the polynomial $x^2 - 3$ is irreducible over $\mathbb{F}_7$, but there it has a root $\alpha$ in its algebraic closure, $\overline{\mathbb{F}_7}$.
-The projective point $(1 :  \alpha : \alpha)$ is a $\overline{\mathbb{F}_7}$-rational point.
+The projective point $(1 :  \alpha : \alpha)$ is a $\overline{\mathbb{F}_7}$-rational point on $\mathfrak C$.
 \end{exmp*}
@@
 \begin{thm}[Bezout's theorem, \cite{Wal00}] %Not word-by-word
-	If $F, G \in K[X, Y, Z]$ are homogeneous polynomials of degrees $d$ and $e$, respectively, then their curves $\mathfrak C_F$ and $\mathfrak C_G$ intersect in exactly $d\cdot e$ $L$-rational points, counting multiplicity.
+	If $F, G \in K[X, Y, Z]$ are homogeneous polynomials and there is no homogeneous polynomial in $K[X, Y, Z]$ that divides both $F$ and $G$, then their curves $\mathfrak C_F$ and $\mathfrak C_G$ intersect in exactly $\deg(F) \cdot \deg(G)$ $L$-rational points, counting multiplicity.
 \end{thm}
@@
 	The \emph{degree} of $D$ is $\sum a_P$.
-	The \emph{support} $\Supp D$ is the set $\{P \in X : a_P \neq 0\}$.
+	The \emph{support} of $D$, denoted by $\Supp D$, is the set of $L$-rational points $P$ on $\mathfrak C$ that satisfy $a_P \neq 0$.
 \end{defn}
 
-\begin{defn}[Field of rational functions on a curve, \cite{Wal00}] %Copied
-	Let $F$ be the polynomial which defines the nonsingular projective plane curve $C$ over the field $\mathbb{F}_q$. The \emph{field of rational functions on $C$} is
-	\begin{equation}
-		\mathbb{F}_q(C) := \left(\left\{\frac{G}{H}\, \bigg|\,\, \makecell{G, H \in \mathbb{F}_q[X, Y, Z]\\\text{are homogeneous}\\\text{of the same degree}} \right\} \cup \{0\}\right) / \sim
-	\end{equation}
-	where $g/h \sim g'/h'$ if, and only if, $gh' - g'h \in \langle F \rangle \subset \mathbb{F}_q[X, Y, Z]$.
-	\todo{Redefine it in a way that actually shows it is pretty simple.}
+%\begin{defn}[Field of rational functions on a curve, \cite{Wal00}] %Copied
+%	Let $F$ be the polynomial which defines the nonsingular projective plane curve $\mathfrak C$ over the field $\mathbb{F}_q$. The \emph{field of rational functions on $C$} is
+%	\begin{equation}
+%		\mathbb{F}_q(\mathfrak C) := \left(\left\{\frac{G}{H}\, \bigg|\,\, \makecell{G, H \in \mathbb{F}_q[X, Y, Z]\\\text{are homogeneous}\\\text{of the same degree}} \right\} \cup \{0\}\right) / \sim
+%	\end{equation}
+%	where $g/h \sim g'/h'$ if, and only if, $gh' - g'h \in \langle F \rangle \subset \mathbb{F}_q[X, Y, Z]$.
+%	\todo{Redefine it in a way that actually shows it is pretty simple.}
+%\end{defn}
+
+\begin{defn}[Riemann--Roch space, \cite{LS87}]
+	If $D = \sum n_p P$, then define the \emph{Riemann--Roch space $\mathcal L(D)$} as the vector space formed by all homogeneous rational functions $f$ such that the order of $f$ at each point $P$ of $\mathfrak C$ is greater or equal to $-n_P$ (plus the zero polynomial).
 \end{defn}
 
-\begin{defn}[\cite{LS87}]
-	If $D = \sum n_p P$, then define the vector space $\mathcal L(D)$ as the set of all homogeneous rational functions $f$ such that the order of $f$ at each point $P$ of $\mathfrak C$ is greater or equal to $-n_P$.
-\end{defn}
+\begin{prop}\label{prop:degDlt0}
+	If $\deg D < 0$, then $\mathcal L(D)$ only contains the zero polynomial.
+\end{prop}
 
-For our study, an important theorem is the following:
+\begin{proof}
+	\todo{Prove this Proposition.}
+\end{proof}
+
+For our study, an important theorem from Algebraic Geometry that will be useful in Section \ref{s:grs} when creating new types of codes is the following one:
 \begin{thm}[Riemman--Roch Theorem, \cite{Wal00}]
@@
 \section{Generalized Reed--Solomon codes} \label{s:grs}
-Let $\mathbb{P}^1(\mathbb{F}_q)$ denote the projective line over $\mathbb{F}_q$.
-We will write $(a : b)$ to denote the projective point corresponding to the $1$-dimensional vector space through $(a, b)$.
+Let $\mathbb{P}^1(\mathbb{F}_q)$ denote the projective line over $\mathbb{F}_q = \{\alpha_1, \dots, \alpha_q\}$.
+We will write $(a : b)$ to denote the projective point corresponding to the $1$-dimensional vector space containing $(a, b)$.
 The points on $\mathbb{P}^1(\mathbb{F}_q)$ are the points
@@
 \begin{equation}
-	RS_q(n, k) = \{f(P_1), f(P_2), \dots, f(P_n) \mid f \in \mathcal L(D)\}.
+	RS_q(n, k) = \left\{\big(f(P_1), f(P_2), \dots, f(P_n)\big) \mid f \in \mathcal L(D)\right\}.
 \end{equation}
@@
 Here, we are evaluating the function $f$ in the points of the projective line.
-We shall generalize the idea by changing the projective line to an arbitrary projective curve, and allowing other divisors $D$.
+We shall generalize the idea by changing the projective line to an arbitrary projective curve, and allowing other divisors.
 
@@
 	Let $\mathfrak C$ be an irreducible nonsingular%
-	\footnote{The adjectives make sure $\mathfrak C$ is well-behaved. The reader should not worry about them.}
+	\footnote{These adjectives just make sure $\mathfrak C$ does not have some weird behavior, e.g., $\mathfrak C$ has no double root. The reader should not worry much about them.}
 %%	\todo{Provide an explanation for why the `irreducible nonsingular' is there, but not a thing that the reader should worry. I think the key is some sort of multiplicity.}
@@
 \begin{proof}
-	\todo{Write proof.}
+	Since $C(\mathfrak C, \mathcal P, D)$ is a subset of $\mathbb{F}_q^n$, it is a code of length $n$.
+
+	Let $\psi: \mathcal L(D) \to \mathbb{F}_q^n$ be defined by $f \mapsto (f(P_1), \dots, f(P_n))$.
+This is a linear transformation, and $\mathcal L(D)$ is a vector space, thus the image of this function, which is precisely $C(\mathfrak C, \mathcal P, D)$, is also a vector space; thus it is a linear code.
+
+	Futhermore, we shall prove that $\psi$ is injective.
+	If $\psi(f) = \psi(g)$, then $\psi(f - g) = \vec 0$.
+	Let $h := f-g$.
+	We have $h(P_1) = h(P_2) = \dots = h(P_n) = 0$, so every $P_i$ is a zero of $h$, and finally $a_{P_i} \ge 1$, for all $1 \le i \le n$.
+	Therefore, $h \in \mathcal L(D - P_1 - \cdots - P_n)$.
+	Since $\deg D < n$, we have $\deg(D - P_1 - \cdots - P_n) < 0$ and, consequenly, $h$ must be the zero polynomial by Proposition \ref{prop:degDlt0}.
+	Therefore, $f = g$, finishing the proof that $\psi$ is injective.
+	Since $\psi$ is a injective linear transformation, the dimension of the domain and of the image are the same.
+	Therefore, the dimension of $C(\mathfrak C, \mathcal P, D)$ is $k = \dim \mathcal L(D)$, which evaluates to $\deg D + 1 - g$ by the Riemman-Roch Theorem.
+
+	Finally, let $f \neq g$ be polynomials such that $\psi(f)$ and $\psi(g)$ yield the minimum distance $d$.
+	Then, $\psi(f) - \psi(g) = \psi(f-g)$ and $\psi(g) - \psi(g) = \vec 0$ also yield the same distance $d$.
+	Therefore, if we define $h = f - g$, exactly  $d$ coordinates of $\psi(h)$ are nonzero.
+	Without loss of generality, say that $h(P_{d+1}) = \cdots = h(P_n) = 0$.
+	Similarly as in the previous paragraph, this implies $h \in \mathcal L(D - P_{d+1} - \cdots - P_n)$.
+	Since $h$ is not the zero polynomial, Proposition \ref{prop:degDlt0} implies $\deg(D - P_{d+1} - \cdots - P_n) = \deg D - (n-d) \ge 0$, i.e., $d \ge n - \deg D$.
 \end{proof}
 
-We want large $R$ and $\delta$, and these codes yield 
+This theorem is an interesting result! We want large $R$ and $\delta$, and these codes yield $k + d \ge n + 1 - g$, i.e., 
 	\begin{equation}
@@
 	\end{equation}
-where $n$ is the number of rational points of a curve $\mathfrak C$, with genus $g$; this is an interesting result!
-All the work done can be applied for algebraic curves in higher dimensional projective spaces.
+where $n$ is the number of rational points of a curve $\mathfrak C$, with genus $g$.
+Futhermore, all the work done can be applied for algebraic curves in higher dimensional projective spaces.
 
@@
 On equation \eqref{eq:g/n}, we observe that good algebraic geometric codes are generated by curves with a small ratio between $g$ and $n$.
-On \cite{TVZ82},\todo{Talk a bit more about it.} the authors present a sequence of such curves, with $g/n$ large enough to create a better bound than the Gilbert--Varshamov one.
+On \cite{TVZ82},\todo{Write one or two more sentences about this article.} the authors present a sequence of such curves, with $g/n$ large enough to create a better bound than the Gilbert--Varshamov one.
 

### 2021-05-06 draft.tex
2021-05-06 Morning Spark

@@
 \usepackage[mathscr]{eucal}
+\usepackage[symbol, perpage]{footmisc}
 
@@
 
-\section{Singleton bound and a promising example} \label{s:singleton}
+\section{The singleton bound and a promising example} \label{s:singleton}
 \begin{thm}[Singleton Bound]\label{thm:singleton_bound}
@@
 	$RS_q(n, k)$ is a subset of $\mathbb{F}_q^n$, thus it has length $n$.  
-	Note that $ L_k$ is a vector space over $\mathbb{F}_q$.
+	Note that $ \mathcal L_k$ is a vector space over $\mathbb{F}_q$.
 	Note that $\{1, x, x^2, \dots, x^{k-1}\}$ is a choice of basis for this vector space, thus it has dimension $k$.
-	Consider the map $\phi:  L_k \to \mathbb{F}_q^n$ given by 
+	Consider the map $\phi:  \mathcal L_k \to \mathbb{F}_q^n$ given by 
 	\begin{equation}
@@
 	Therefore, $\phi$ is also injective.
-	This implies that the dimension of the domain $ L_k$ is the same as the dimension of the image $RS_q(n, k)$, i.e.,  $\dimension RS_q(n, k) = k$.
+	This implies that the dimension of the domain $ \mathcal L_k$ is the same as the dimension of the image $RS_q(n, k)$, i.e.,  $\dimension RS_q(n, k) = k$.
 
-	Finally, consider distinct $f, g \in  L_k$ and define $d = \dist(\phi(f), \phi(g))$, $f - g$ has at least $n - d$ roots.
+	Finally, consider distinct $f, g \in  \mathcal L_k$ and define $d = \dist(\phi(f), \phi(g))$, $f - g$ has at least $n - d$ roots.
 	Furthermore, $f - g$ is a non-zero polynomial with degree less than $k$, thus has at most $k - 1$ roots.
 	Then,  $ k - 1 \ge \#\ \text{roots} \ge n - d$.
-	If we choose $f, g$ such that $d$ is the minimal distance, we get $k + d_{\mathrm{min}} \ge n + 1$, which together with \nameref{thm:singleton_bound} implies $k + d_\text{min} = n + 1$.
+	If we choose $f, g$ such that $d$ is the minimal distance, we get $k + d_{\mathrm{min}} \ge n + 1$, which together with the Singleton Bound, implies $k + d_\text{min} = n + 1$.
 \end{proof}
@@
 
-\section{Curves, Rational Functions and Divisors}
+\section{Curves, rational functions and divisors}
 
@@
 
-\begin{defn}[Rational function]
-	A rational function $f$ over $K$ is the ratio $g/h$ of polynomials $g, h \in K[x, y]$.
-	A homogeneous rational function $F$ over a $K$ is the ratio $G/H$ of homogeneous polynomials $G, H \in K[x, y]$.
+%\begin{defn}[Rational function]
+%	A rational function $f$ over $K$ is the ratio $g/h$ of polynomials $g, h \in K[x, y]$.
+%	A homogeneous rational function $F$ over a $K$ is the ratio $G/H$ of homogeneous polynomials $G, H \in K[x, y]$.
+%
+%	After cancelling common roots of $g, h$, the roots of $g$ are called \emph{zeros} of $f$ and the roots of $h$ are called the \emph{poles} of $f$.  
+%	We say $f$ has order $n$ at $P$ if $P$ is a zero of multiplicity $n$; order $-n$ if $P$ is a pole with multiplicity $n$; and order $0$, otherwise.
+%\end{defn}
 
-	After cancelling common roots of $g, h$, the roots of $g$ are called \emph{zeros} of $f$ and the roots of $h$ are called the \emph{poles} of $f$.  
-	We say $f$ has order $n$ at $P$ if $P$ is a zero of multiplicity $n$; order $-n$ if $P$ is a pole with multiplicity $n$; and order $0$, otherwise.
+\begin{defn}[Rational function on a curve]
+	Let $F \in K[X, Y, Z]$ be a homogeneous polynomial and let $\mathfrak C = \mathfrak C_F$.
+	If $G, H \in K[X, Y, Z]$ are homogeneous polynomials of equal degree, then the fraction $G/H$ is called a \emph{rational function} on $\mathfrak C$.
+	Fractions $G/H$ and $G'/H'$ define the same rational function if $G'H - GH'$ is a multiple of $F$, i.e., if  $G'H - GH'$ vanishes at all $L$-rational points on $\mathfrak C$.
 \end{defn}
+
+	Note that it makes sense to evaluate a rational function on a projective point, since \[
+		\frac{G(X_0, Y_0, Z_0)}{H(X_0, Y_0, Z_0)} = \frac{\lambda^d G(X_0, Y_0, Z_0)}{\lambda^d H(X_0, Y_0, Z_0)} = \frac{G(\lambda X_0, \lambda Y_0, \lambda Z_0)}{H(\lambda X_0, \lambda Y_0, \lambda Z_0)},
+	\]
+	i.e., the result is the same regardless of the representation of a given projective point.
+
+	After cancelling common factors of $G$ and $H$, a $L$-rational point $P$ on $\mathfrak C$ is called a \emph{zero} of $G/H$ whenever $G$ vanishes at $P$, and is called a \emph{poles} of $G/H$ whenever $H$ vanishes at $P$.
+	We say $G/H$ has order $n$ at $P$ if $P$ is a zero of multiplicity $n$; order $-n$ if $P$ is a pole with multiplicity $n$; and order $0$, otherwise.
 
@@
 
-\begin{defn}[Riemann--Roch space, \cite{LS87}]
-	If $D = \sum n_p P$, then define the \emph{Riemann--Roch space $\mathcal L(D)$} as the vector space formed by all homogeneous rational functions $f$ such that the order of $f$ at each point $P$ of $\mathfrak C$ is greater or equal to $-n_P$ (plus the zero polynomial).
+\begin{defn}[\cite{LS87}]
+	If $D = \sum n_p P$, then define $\mathcal L(D)$ as the vector space formed by all homogeneous rational functions $f$ such that the order of $f$ at each $L$-rational point $P$ on $\mathfrak C$ is greater or equal to $-n_P$ (plus the zero polynomial).
 \end{defn}
@@
 \begin{proof}
-	\todo{Prove this Proposition.}
+	Bezout's theorem implies that $\mathfrak C$ and $\mathfrak C_G$ intersect in the same number of points, counting multiplicity, than $\mathfrak C$ and $\mathfrak C_H$.
+Therefore, the number of zeros of a function is the same as the number of poles, counting multiplicity.
+Thus, the sum of the orders of $G/H$ at the $L$-rational points on $\mathfrak C$ must be zero.
+On the other hand, if $G/H \in \mathcal L(D)$, then the sum of the orders of $G/H$ at the $L$-rational points on $\mathfrak C$ must be $\ge - \deg(D)$.
+
+	Thus, if $\deg(D) < 0$, then a rational function $G/H$ cannot be in $\mathcal L(D)$.
 \end{proof}
@@
 For our study, an important theorem from Algebraic Geometry that will be useful in Section \ref{s:grs} when creating new types of codes is the following one:
-\begin{thm}[Riemman--Roch Theorem, \cite{Wal00}]
+\begin{thm}[Riemann--Roch Theorem, \cite{Wal00}]
 	Let $\mathfrak C$ be a nonsingular projective curve of genus%
@@
 
-\begin{prop}
-	The sets $L_k$ and $\mathcal L(D)$ are mapped with a bijection (homogenization) $\phi: f(x) \mapsto Y^{\deg f} f(X/Y)$.
-\end{prop}
-\begin{proof}
-	\todo{Write proof.}
-\end{proof}
+Note that, if a polynomial $f(x) \in \mathcal L_k$ has degree $d < k$, then the rational function \[
+	F(X, Y) = \frac{Y^d f(X/Y)}{Y^d}
+\]
+has $P_\infty$ as its only pole, with order at most $k-1$. Thus, $F(X, Y) \in \mathcal L(D)$ and $f(\alpha_i) = F(P_i)$ for any $\alpha_i$.
 
@@
 	Let $\mathfrak C$ be an irreducible nonsingular%
-	\footnote{These adjectives just make sure $\mathfrak C$ does not have some weird behavior, e.g., $\mathfrak C$ has no double root. The reader should not worry much about them.}
+	\footnote{These adjectives just make sure $\mathfrak C$ does not have some weird behavior%
+	%, e.g., $\mathfrak C$ has no double root%
+	. The reader should not worry much about them.}
 %%	\todo{Provide an explanation for why the `irreducible nonsingular' is there, but not a thing that the reader should worry. I think the key is some sort of multiplicity.}
@@
 	Since $\psi$ is a injective linear transformation, the dimension of the domain and of the image are the same.
-	Therefore, the dimension of $C(\mathfrak C, \mathcal P, D)$ is $k = \dim \mathcal L(D)$, which evaluates to $\deg D + 1 - g$ by the Riemman-Roch Theorem.
+	Therefore, the dimension of $C(\mathfrak C, \mathcal P, D)$ is $k = \dim \mathcal L(D)$, which evaluates to $\deg D + 1 - g$ by the Riemann-Roch Theorem.
 

### 2021-05-06 draft.tex
2021-05-06 afternoon review update

@@
 
-Suppose Alice wants to send a message to Bob though a noisy channel.
-When Bob receives the message, it is possible that some of the information is misinterpreted.
-For example, if Alice sends the message `\texttt{food}' through the noisy channel, one of its letters may be misinterpreted and Bob could actually receive `\texttt{\underline{m}ood}'.
+Suppose Alice wants to send a message to Bob through a noisy channel.
+When Bob receives the message, it is possible that some of the information is distorted.
+For example, if Alice sends the message `\texttt{I am sad!}' through the noisy channel, one of its letters may be misinterpreted and Bob could actually receive the message `\texttt{I am \underline{m}ad!}'.
 So, the question Coding Theory tries to answer is:
@@
 
-We will provide the proof for Theorem \ref{thm:singleton_bound} when $C$ is a linear code over a field $K$.
+We will provide the proof for Theorem \ref{thm:singleton_bound} when $C$ is a linear code over a field $K$, but bear in mind that the theorem is true for any code $C$.
 
@@
 	Let $q$ be a power of a prime, and $\mathbb{F}_q = \{\alpha_1, \alpha_2, \dots, \alpha_q\}$ the field with $q$ elements.
-	Let $k$ be an integer, and ${L}_k$ the set of all polynomials over $\mathbb{F}_q$ with degree smaller than $k$.
+	Let $k$ be a positive integer, and $\mathcal L_k$ the set of all polynomials over $\mathbb{F}_q$ with degree smaller than $k$.
 	Let $k \le n \le q$ be an integer. The Reed--Solomon code $RS_q(n, k)$ over $\mathbb{F}_q$ is 
 	\begin{equation}
-		RS_q(n, k) = \left\{\left(f(\alpha_1), f(\alpha_2), \dots, f(\alpha_n)\right) \mid f \in {L}_k\right\}.
+		RS_q(n, k) = \left\{\left(f(\alpha_1), f(\alpha_2), \dots, f(\alpha_n)\right) \mid f \in \mathcal L_k\right\} \subset \mathbb{F}_q^n.
 	\end{equation}
@@
 \begin{proof}
-	$RS_q(n, k)$ is a subset of $\mathbb{F}_q^n$, thus it has length $n$.  
-	Note that $ \mathcal L_k$ is a vector space over $\mathbb{F}_q$.
-	Note that $\{1, x, x^2, \dots, x^{k-1}\}$ is a choice of basis for this vector space, thus it has dimension $k$.
+	$RS_q(n, k)$ is a subset of $\mathbb{F}_q^n$, thus it is a code with length $n$.  
+	Note that $ \mathcal L_k$ is a vector space over $\mathbb{F}_q$, and $(1, x, x^2, \dots, x^{k-1})$ is a choice of basis for this vector space, thus it has dimension $k$.
 	Consider the map $\phi:  \mathcal L_k \to \mathbb{F}_q^n$ given by 
 	\begin{equation}
-		f \mapsto (f(\alpha_1), f(\alpha_2), \dots, f(\alpha_n)).
+		f \mapsto (f(\alpha_1), f(\alpha_2), \dots, f(\alpha_n)),
 	\end{equation}
-
-	Note that the map $\phi$ is a linear transformation.
+	which is a linear transformation.
 	Thus, its image $\Ima \phi = RS_q(n, k)$ is also a vector space.  
@@
 
-	Finally, consider distinct $f, g \in  \mathcal L_k$ and define $d = \dist(\phi(f), \phi(g))$, $f - g$ has at least $n - d$ roots.
+	Finally, consider $f \neq g \in  \mathcal L_k$ and define $d = \dist(\phi(f), \phi(g))$, $f - g$ has at least $n - d$ roots.
 	Furthermore, $f - g$ is a non-zero polynomial with degree less than $k$, thus has at most $k - 1$ roots.
 	Then,  $ k - 1 \ge \#\ \text{roots} \ge n - d$.
-	If we choose $f, g$ such that $d$ is the minimal distance, we get $k + d_{\mathrm{min}} \ge n + 1$, which together with the Singleton Bound, implies $k + d_\text{min} = n + 1$.
+	If we choose $f$ and $g$ such that $d$ is the minimal distance, we get $k + d_{\mathrm{min}} \ge n + 1$, which together with the Singleton Bound, implies $k + d_\text{min} = n + 1$.
 \end{proof}
 
-The Reed--Solomon codes are very good codes in the sense that they have the largest possible sum $k + d$ for their length $n$.
-However, Reed--Solomon codes are limited because their length is at most the alphabet size.
+The Reed--Solomon codes are very good codes in the sense that they have the largest possible sum $k + d$ for their length.
+This is guaranteed by the Singleton Bound.
+
+However, Reed--Solomon codes are limited because their length is at most their alphabet size.
 So, a question naturally arises: Given fixed $\mathbb{F}_q$, are there codes over $\mathbb{F}_q$ with arbitrarily large $n$ and $R + \delta = 1 + 1/n$?
@@
 \end{equation}
-The article \cite{TVZ82} uses Algebraic Geometry to show that there are codes that give better bounds.
+However, the article \cite{TVZ82} uses structures from Algebraic Geometry to create new codes and show that they (sometimes) give better bounds.
 
@@
 
+Before understanding the codes from \cite{TVZ82}, we need to familiarize with some tools in Algebraic Geometry.
 Through this section, let $K$ be a field and $L$ its algebraic closure.
@@
 
-Note that there exists a natural injection, called \emph{homogenization}, from the set of polynomials in $K[x, y]$ and the set of homogeneous polynomials in $K[X, Y, Z]$ defined by $f(x, y) \mapsto Z^{\deg f}f(X/Z, Y/Z)$.
-Because of this, we'll denote by $\mathfrak C$ both $\mathfrak C_f$ and $\mathfrak C_F$, where the usage is clear by context.
+Note that there exists a natural injection, called \emph{homogenization}, from the set of polynomials in $K[x, y]$ to the set of homogeneous polynomials in $K[X, Y, Z]$ defined by $f(x, y) \mapsto Z^{\deg f}f(X/Z, Y/Z)$.
+Because of this, we'll denote both $\mathfrak C_f$ and $\mathfrak C_F$ by $\mathfrak C$, where the usage is clear by context.
 
@@
 	The point $(1 : 2 : 3)$ is a $\mathbb{F}_7$-rational point on $\mathfrak C$.
-	Note that the polynomial $x^2 - 3$ is irreducible over $\mathbb{F}_7$, but there it has a root $\alpha$ in its algebraic closure, $\overline{\mathbb{F}_7}$.
+	Note that the polynomial $x^2 - 3$ is irreducible over $\mathbb{F}_7$, but there is a root $\alpha$ in its algebraic closure, $\overline{\mathbb{F}_7}$.
 The projective point $(1 :  \alpha : \alpha)$ is a $\overline{\mathbb{F}_7}$-rational point on $\mathfrak C$.
 \end{exmp*}
+
+One of the most important theorems in Algebraic Geometry, that we will use in this paper, is the following one:
 
@@
 
-\begin{defn}[Rational function on a curve]
+\begin{defn}[Rational function on a curve, \cite{TVN07}]
 	Let $F \in K[X, Y, Z]$ be a homogeneous polynomial and let $\mathfrak C = \mathfrak C_F$.
@@
 
-	Note that it makes sense to evaluate a rational function on a projective point, since \[
-		\frac{G(X_0, Y_0, Z_0)}{H(X_0, Y_0, Z_0)} = \frac{\lambda^d G(X_0, Y_0, Z_0)}{\lambda^d H(X_0, Y_0, Z_0)} = \frac{G(\lambda X_0, \lambda Y_0, \lambda Z_0)}{H(\lambda X_0, \lambda Y_0, \lambda Z_0)},
+	Note that it makes sense to evaluate a rational function on a projective point, since the result is the same regardless of the representation of the projective point, i.e.,  \[
+		\frac{G(X_0, Y_0, Z_0)}{H(X_0, Y_0, Z_0)} = \frac{\lambda^d G(X_0, Y_0, Z_0)}{\lambda^d H(X_0, Y_0, Z_0)} = \frac{G(\lambda X_0, \lambda Y_0, \lambda Z_0)}{H(\lambda X_0, \lambda Y_0, \lambda Z_0)}.
 	\]
-	i.e., the result is the same regardless of the representation of a given projective point.
 
-	After cancelling common factors of $G$ and $H$, a $L$-rational point $P$ on $\mathfrak C$ is called a \emph{zero} of $G/H$ whenever $G$ vanishes at $P$, and is called a \emph{poles} of $G/H$ whenever $H$ vanishes at $P$.
+	After cancelling common factors of $G$ and $H$, a $L$-rational point $P$ on $\mathfrak C$ is called a \emph{zero} of $G/H$ whenever $G$ vanishes at $P$, and is called a \emph{pole} of $G/H$ whenever $H$ vanishes at $P$.
 	We say $G/H$ has order $n$ at $P$ if $P$ is a zero of multiplicity $n$; order $-n$ if $P$ is a pole with multiplicity $n$; and order $0$, otherwise.
@@
 	Let $\mathfrak C$ be a projective plane curve defined over $K$.
-	A \emph{divisor} $D$ on $\mathfrak C$ is a formal finite sum of the form $D = \sum a_P P$, where $P$ varies over the $L$-rational points on $\mathfrak C$, $a_P$ is an integer and $a_P = 0$ for all but finitely many points $P$.
+	A \emph{divisor} $D$ on $\mathfrak C$ is a formal finite sum of the form $D = \sum a_P P$, where the sum varies over all $L$-rational points $P$ on $\mathfrak C$, $a_P$ is an integer and $a_P = 0$ for all but finitely many $L$-rational points $P$ in $\mathfrak C$.
+
 	The \emph{degree} of $D$ is $\sum a_P$.
@@
 \begin{defn}[\cite{LS87}]
-	If $D = \sum n_p P$, then define $\mathcal L(D)$ as the vector space formed by all homogeneous rational functions $f$ such that the order of $f$ at each $L$-rational point $P$ on $\mathfrak C$ is greater or equal to $-n_P$ (plus the zero polynomial).
+	If $D = \sum a_p P$, then define $\mathcal L(D)$ as the vector space formed by all homogeneous rational functions $f$ such that the order of $f$ at each $L$-rational point $P$ on $\mathfrak C$ is greater or equal to $-a_P$ (plus the zero polynomial).
 \end{defn}
@@
 	Bezout's theorem implies that $\mathfrak C$ and $\mathfrak C_G$ intersect in the same number of points, counting multiplicity, than $\mathfrak C$ and $\mathfrak C_H$.
-Therefore, the number of zeros of a function is the same as the number of poles, counting multiplicity.
+Therefore, the number of zeros of a rational function $G/H$ is the same as the number of poles, counting multiplicity.
 Thus, the sum of the orders of $G/H$ at the $L$-rational points on $\mathfrak C$ must be zero.
@@
 \section{Generalized Reed--Solomon codes} \label{s:grs}
-Let $\mathbb{P}^1(\mathbb{F}_q)$ denote the projective line over $\mathbb{F}_q = \{\alpha_1, \dots, \alpha_q\}$.
+Let's now contextualize Reed--Solomon codes inside Algebraic Geometry.
+
+Let $\mathbb{P}^1(\mathbb{F}_q)$ be the projective line over $\mathbb{F}_q = \{\alpha_1, \dots, \alpha_q\}$.
 We will write $(a : b)$ to denote the projective point corresponding to the $1$-dimensional vector space containing $(a, b)$.
-The points on $\mathbb{P}^1(\mathbb{F}_q)$ are the points
+Thus, the points on $\mathbb{P}^1(\mathbb{F}_q)$ are
 \begin{equation}
@@
 
-Consider the divisor $D = (k-1)P_\infty$ and the associated vector space $\mathcal L(D)$, which can be seen as the set of two-variable homogeneous rational functions which have a pole of order less than $k$ in the point $P_\infty$.
+Consider the divisor $D = (k-1)P_\infty$ and the associated vector space $\mathcal L(D)$, which can be understood as the set of two-variable homogeneous rational functions which can only have a pole at $P_\infty$, and with order at most $k-1$.
 
@@
 \]
-has $P_\infty$ as its only pole, with order at most $k-1$. Thus, $F(X, Y) \in \mathcal L(D)$ and $f(\alpha_i) = F(P_i)$ for any $\alpha_i$.
+has $P_\infty$ as its only pole, with order at most $k-1$. Thus, $F(X, Y) \in \mathcal L((k-1)P_\infty)$ and $f(\alpha_i) = F(P_i)$ for any $\alpha_i$.
 
-Then, we can rewrite the Reed--Solomon code from Definition \ref{defn:rs_codes} as
+On the other hand, any $G/H \in \mathcal L((k-1)P_\infty)$ has $H = Y^d$ with $d < k$ (since the only pole is $P_\infty$) and, therefore, $G$ is a homogeneous polynomial with degree $d$.
+Thus, $G/H(P_i) = G(\alpha_i, 1)$, which is an one-variable polynomial with degree less than $k$.
+
+Therefore, because of this bijection between $\mathcal L_k$ and $\mathcal L((k-1)P_\infty)$, we can rewrite the Reed--Solomon code from Definition \ref{defn:rs_codes} as
 \begin{equation}
-	RS_q(n, k) = \left\{\big(f(P_1), f(P_2), \dots, f(P_n)\big) \mid f \in \mathcal L(D)\right\}.
+	RS_q(n, k) = \left\{\big(f(P_1), f(P_2), \dots, f(P_n)\big) \mid f \in \mathcal L((k-1)P_\infty)\right\}.
 \end{equation}
@@
 Suppose $D$ satisfies $2g - 2 < \deg D < n$.
-Then the algebraic geometric code $C(\mathfrak C, \mathcal P, D)$ is linear of:
-	\begin{enumerate}[label = \textbullet, itemsep = 0pt]
-		\item length $n$,
-		\item dimension $\deg D + 1 - g$,
-		\item minimum distance $d \ge n - \deg D$.
-	\end{enumerate}
+Then the algebraic geometric code $C(\mathfrak C, \mathcal P, D)$ is a linear code with
+length $n$,
+dimension $\deg D + 1 - g$, and 
+minimum distance $d \ge n - \deg D$.
 \end{thm}
@@
 	\end{equation}
-where $n$ is the number of rational points of a curve $\mathfrak C$, with genus $g$.
+where $n$ is the number of rational points of the curve $\mathfrak C$ with genus $g$.
 Futhermore, all the work done can be applied for algebraic curves in higher dimensional projective spaces.
@@
 On equation \eqref{eq:g/n}, we observe that good algebraic geometric codes are generated by curves with a small ratio between $g$ and $n$.
-On \cite{TVZ82},\todo{Write one or two more sentences about this article.} the authors present a sequence of such curves, with $g/n$ large enough to create a better bound than the Gilbert--Varshamov one.
+On \cite{TVZ82}, 
+%\todo{Write one or two more sentences about this article.}
+the authors present a sequence of such curves, with $g/n$ large enough to create a better bound than the Gilbert--Varshamov one.
 
